---
title: "Future"
author: "Sofie McComb"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##Load Packages

```{r}

library(tidyverse)

```


## Data Processing

###Future NLCD Data

Prepared future nlcd data with fragstats calculations on the online R server for faster processing and memory storage. The R scripts used can be found under the server, and the R scripts can be found stored under the R/Future folder as NF_Future and NLCD_Future. NF_Future is the function created to do all the computation, and NLCD_Future carries our the function for the different desired years and gets the NLCD in an appropriate spreadsheet format. Will just put in the saved csvs below, where they were transfered from the online server.

### Compare Results using Future vs Present

```{r}

# #Read in the NLCD files and rbind (works for now-only files are 2006, 2011, 2016-change later if nessary)
#   file_names <- dir("Data/Future/DataProcessing/nlcd", pattern = ".csv", full.names = TRUE) #files located per year
#   nlcd <- do.call(rbind,lapply(file_names,readr::read_csv))
# 
# 
# #Change years to match those in the other datasets so can combine by FIPS and years
#   #2001 to 2002, 2006 to 2007, 2011 to 2012, and 2016 to 2017
#   nlcd$Year[nlcd$Year==2006] <- 2007
#   nlcd$Year[nlcd$Year==2011] <- 2012
#   nlcd$Year[nlcd$Year==2016] <- 2017
# 
# #Write final nlcd data to be used in combination with other dataframes
#   write_csv(nlcd, "Data/Future/DataProcessing/df/nlcd.csv")
  
#Read in nlcd
nlcd<-read_csv("Data/Future/DataProcessing/df/nlcd.csv")

#Read in other datasets from dataprocessing to create comparable fulldata_future dataset
    coa<-read_csv("Data/DataProcessing/df/coa.csv")
    cdl<-read_csv("Data/DataProcessing/df/cdl.csv")
    #Read in ERS file, to be combined with other data as is
    ERS<-readxl::read_xls("Data/DataProcessing/ERS/ERSRegions_To_Counties.xls")
    ERS<-ERS[,1:3]
    colnames(ERS)<-c("FIPS", "ERSCode", "ERSName")
    #Read in ASD file, to be combined with the other data as is
    ASD<-readr::read_csv("Data/DataProcessing/ASD/ASD_County_Crosswalk.csv") %>% 
      select(statecountyfips, StateASD)
    colnames(ASD)<-c("FIPS", "ASDCode")


#Make FIPS numeric for nlcd to match with other datasets
nlcd$FIPS<-as.numeric(nlcd$FIPS)
    
#Make fulldata_future
    #List and merge three datasets by the unique combination of FIPS and Year Values
fulldata<-list(coa, cdl, nlcd) %>% 
  reduce(full_join, by=c("FIPS", "Year"))

#Merge with ERS and ASD by just FIPS
fulldata<-list(fulldata, ERS, ASD) %>% 
  reduce(full_join, by=c("FIPS"))


#Drop the 9 VA counties 51515, 51530, 51580, 51595, 51600, 51610, 51678,51685, 51720 
  #that had NA in CDL and that are essentially within other counties
fulldata<-fulldata %>%
  filter(!(FIPS==51515)&!(FIPS==51530)&!(FIPS==51580)&!(FIPS==51595)&!(FIPS==51600)&
           !(FIPS==51610)&!(FIPS==51678)&!(FIPS==51685)&!(FIPS==51720))

#Use 2017 county area to fill all other year county area so standardized per FIPS
  fulldata<-fulldata %>% 
    dplyr::group_by(FIPS) %>% 
    arrange(desc(Year)) %>% 
    dplyr::mutate(countyarea=countyarea[1]) %>% 
    arrange(FIPS) %>% 
    dplyr::ungroup()

fulldata<-fulldata %>% 
  dplyr::mutate(cropintensity=harvcrop/((pland_crops/100)*countyarea)) %>% 
  dplyr::mutate(natural_crops_ed=tel_naturalcrops_nc/(countyarea*0.4046856422)) %>% #meters shared edge per hectare county area
  dplyr::mutate(forest_crops_ed=tel_forestcrop_fc/(countyarea*0.4046856422)) %>% 
  dplyr::mutate(shrubgrass_crops_ed=tel_shrubgrasscrop_sgc/(countyarea*0.4046856422))

#Replace infinite values with NA for regression 
  fulldata$cropintensity[sapply(fulldata$cropintensity, is.infinite)]<-NA
  fulldata$natural_crops_ed[sapply(fulldata$natural_crops_ed, is.infinite)]<-NA
  
#If harvcrop or pland_crops is 0 then make cropintensity 0 
  fulldata$cropintensity<- ifelse(fulldata$harvcrop==0, 0, fulldata$cropintensity)
  fulldata$cropintensity<- ifelse(fulldata$pland_crops==0, 0, fulldata$cropintensity)
  
#Remove rows with NA value for year
  fulldata<-fulldata[!is.na(fulldata$Year),]
  
#Name as fulldata_future
  fulldata_future<-fulldata
    
#Write fulldata to df folder as all data pulled together
    write_csv(fulldata_future, "Data/Future/DataProcessing/df/fulldata_future.csv")
    save(fulldata_future, file = "Data/Future/DataProcessing/df/fulldata_future.rda")


    
    
##############
#Visualize with Boxplots
    #Source R script to create boxplot visualizations
load("Data/Future/DataProcessing/df/fulldata_future.rda")
#This script develops a function to create boxplots of variable trends over time.

  #The function is used in the Visualize.Rmd.

#Load necessary packages
library(ggplot2)
#Example of function use: var_boxplot(variable=fulldata$insect_planted, yaxis="Prop.Cropland with Insecticides")

var_boxplot<-function(variable, yaxis){
  #Create Boxplot 
  plot<-ggplot(fulldata_future, aes(x=factor(Year), y=variable)) + 
    geom_boxplot(colour="#1F3552", fill="#4271AE", size=1, notch=TRUE)+
    scale_y_continuous(name=yaxis)+
    scale_x_discrete(name="Year")+
    theme_light()+
    theme(panel.grid.major = element_line(colour = "#d3d3d3"),
          panel.grid.minor = element_blank(),
          axis.text=element_text(colour="black", size = 12),
          axis.title=element_text(colour="black", size = 16),
          axis.line = element_line(size=0.5, colour = "black"))
  return(plot)
}


#Create boxplots for variables of interest (NA values will be removed)
insect_plot<-var_boxplot(variable=fulldata_future$insect_planted, yaxis="Prop. Cropland w/ Insecticides")
plandcrops_plot<-var_boxplot(variable=fulldata_future$pland_crops, yaxis="Prop. of Cty in Cropland")
edgecrops_plot<-var_boxplot(variable=fulldata_future$ed_crops, yaxis="Crop Edge Density (m/ha)")
mnacrops_plot<-var_boxplot(variable=fulldata_future$mna_crops, yaxis="Avg. Acreage of Crop Patches (ha)")
largefarm_plot<-var_boxplot(variable=fulldata_future$largefarm_planted, yaxis="Prop. of Cropland with Lg. Farms")
soygrain_plot<-var_boxplot(variable=fulldata_future$soysmallgrain_planted, yaxis="Prop. Soybeans & Sm. Grains")
corn_plot<-var_boxplot(variable=fulldata_future$corn_planted, yaxis="Prop. Corn")
fruitveg_plot<-var_boxplot(variable=fulldata_future$fruitveg_planted, yaxis="Prop. Fruit & Veg.")
msidi_plot<-var_boxplot(variable=fulldata_future$msidi, yaxis="Landscape Diversity")
SDI_plot<-var_boxplot(variable=fulldata_future$SDI, yaxis="Crop Diversity")
ncedge_plot<-var_boxplot(variable=fulldata_future$natural_crops_ed, yaxis="Natural to Crop Land Edges")
fcedge_plot<-var_boxplot(variable=fulldata_future$forest_crops_ed , yaxis="Forest to Crop Land Edges")
sgcedge_plot<-var_boxplot(variable=fulldata_future$shrubgrass_crops_ed , yaxis="Shrubland and Grassland to Crop Land Edges")

#Save insecticides plot
ggexport(insect_plot, filename = "Data/Future/Visualize/boxplots/insecticides_timetrends_boxplots_future.png")

#Arrange boxplots on one page
allvarplots<-ggarrange(plandcrops_plot,edgecrops_plot,
              mnacrops_plot, largefarm_plot, 
              soygrain_plot, corn_plot, fruitveg_plot,
              msidi_plot,SDI_plot, 
             ncedge_plot, fcedge_plot, sgcedge_plot,
          labels = c("A", "B", "C", "D", "E", "F", "G", "H", "I", "J", "K"),
          ncol = 4, nrow = 3)

#Save the combined variable boxplots page
ggexport(allvarplots, filename = "Data/Future/Visualize/boxplots/allvariables_timetrends_boxplots_future.png",
          width = 1800, height = 1500)

    
###############################################
load("Data/Future/DataProcessing/df/fulldata_future.rda")
#Load the needed packages (install first if necessary)
library(ggplot2) #data visualization
library(ggpubr)#To arrange ggplots on a page
library(stringr)#String detection
library(tidyverse) #Datatable manipulation (all functions)
library(dotwhisker) #relabel predictors
library(stargazer) #Create stargazer tables
library(clubSandwich) #For coeftest
#Perform Natural Model for Comparison
data_natural<-fulldata_future %>% 
  select(FIPS, Year, ASDCode, ERSCode,
         insect_planted, pland_crops, natural_crops_ed, mna_crops, largefarm_planted,
         soysmallgrain_planted, corn_planted, fruitveg_planted,
         msidi, SDI) %>% 
    filter(!Year==2002)%>% #Only 3 years of data
  na.omit() %>% #8939 observations (match crops_3yrs and diversity)
  mutate_at(scale, .vars=vars(-FIPS, -Year, -ERSCode, -ASDCode, -insect_planted)) %>%  #Scale by subtracting column mean and dividing by column SD
    rename(Insecticide=insect_planted,
         PercentCrop=pland_crops,
         NaturalCropEdge=natural_crops_ed,
         MeanCropArea=mna_crops,
         LargeFarms=largefarm_planted,
         SoyGrains=soysmallgrain_planted,
         Corn=corn_planted,
         FruitVeg=fruitveg_planted,
         LandDiversity=msidi,
         CropDiversity=SDI)


lm_natural<-lm(Insecticide~PercentCrop+NaturalCropEdge+MeanCropArea+LargeFarms+
                  SoyGrains+Corn+FruitVeg+LandDiversity+CropDiversity+
                  factor(Year)+factor(ASDCode), data=data_natural)
df_natural<-broom::tidy(lm_natural) %>% 
  mutate(model="natural") %>% 
  dplyr::filter(!stringr::str_detect(term, "(Intercept)"),
                !stringr::str_detect(term, "factor"))
df_coef_natural<-lm_natural %>% 
  clubSandwich::coef_test(vcov = "CR2", cluster = data_natural$ASDCode, test = "Satterthwaite") %>% 
  tibble::rownames_to_column(var = "term") %>% 
  rename(estimate=beta, std.error=SE, statistic=tstat, p.value=p_Satt) %>% 
  dplyr::mutate(model="natural") %>% 
  dplyr::filter(!stringr::str_detect(term, "(Intercept)"),
                !stringr::str_detect(term, "factor"))
vif_natural<-rownames_to_column(as.data.frame(car::vif(lm_natural)), "term") %>% 
    dplyr::mutate(model="natural") 

#Plot diversity on x and coefficient on y with SD facet by term
#Relabel predictors
natural_plot_df <- df_coef_natural %>%
  relabel_predictors(c(PercentCrop = "Percent Cropland",
                       NaturalCropEdge= "Natural Crop Edge Density",
                       MeanCropArea = "Avg. Crop Area",
                       LargeFarms = " Proportion Large Farm",
                       SoyGrains= "Proportion Soy & Grains",
                       Corn= "Proportion Corn",
                       FruitVeg= "Proportion Fruit & Veg",
                       LandDiversity= "Landscape Diversity",
                       CropDiversity="Cropland Diversity"))
natural_compare<-ggplot2::ggplot(natural_plot_df, aes(y=fct_rev(as_factor(term)))) +
  geom_errorbarh(aes(xmax = estimate + (1.96*std.error), xmin = estimate - (1.96*std.error)),
                height=0.3, size=1, colour="royalblue")+
  geom_point(aes(x=estimate), size=2, colour="royalblue")+
  geom_vline(xintercept = 0, colour = "grey60", linetype = 2) +
  theme_bw() + ylab("")+xlab("Coefficient Estimate")+
  theme(text = element_text(size = 20))

  ggexport(natural_compare, filename = "Data/Future/Visualize/boxwhisker/natural.png",
           width = 900, height = 800)
  
  
  df_coef_natural<-lm_natural %>% 
  clubSandwich::coef_test(vcov = "CR2", cluster = data_natural$ASDCode, test = "Satterthwaite")
  
  #Natural
stargazer(lm_natural, omit=c("ASDCode","Year"), 
          type = 'text', out = 'Data/Future/Visualize/stargazer/natural_table.txt',
          covariate.labels=c("Percent Cropland", "Natural Crop Edge Density", "Average Crop Area", "Proportion Large Farms", 
                             "Proportion soybeans and small grains", "Proportion corn", "Proportion fruit and vegetables",
                             "Landscape Diversity", "Cropland Diversity"),
          omit.stat=c("LL","ser","f"), 
          se = list(df_coef_natural[,2]),
          p=list(df_coef_natural[,5]))

#Save future datasets as future in order to combine
lm_natural_future<-lm_natural
df_coef_natural_future<-df_coef_natural

#Combine stargazer with old results
load("Data/Analysis/models/lm_natural.Rda")
load("Data/Analysis/models/df/data_natural.Rda")
df_coef_natural<-lm_natural %>% 
  clubSandwich::coef_test(vcov = "CR2", cluster = data_natural$ASDCode, test = "Satterthwaite")

#Compare
  #Natural
stargazer(lm_natural, lm_natural_future, omit=c("ASDCode","Year"), 
          type = 'text', out = 'Data/Future/Visualize/stargazer/natural_table_comparewithpresent.txt',
          covariate.labels=c("Percent Cropland", "Natural Crop Edge Density", "Average Crop Area", "Proportion Large Farms", 
                             "Proportion soybeans and small grains", "Proportion corn", "Proportion fruit and vegetables",
                             "Landscape Diversity", "Cropland Diversity"),
          omit.stat=c("LL","ser","f"), 
          se = list(df_coef_natural[,2],df_coef_natural_future[,2]),
          p=list(df_coef_natural[,5],df_coef_natural_future[,5]),
          column.labels=c("Present NLCD", "Forecast NLCD"), model.numbers=FALSE)

    
    
```



### Test with 5 years of data
But only create lm_test on it to try to figure out best model?

```{r}

#Read in the NLCD files and rbind (works for now-only files are 2006, 2011, 2016-change later if nessary)
  file_names <- dir("Data/Future/DataProcessing/nlcd", pattern = ".csv", full.names = TRUE) #files located per year
  nlcd <- do.call(rbind,lapply(file_names,readr::read_csv))


#Change years to match those in the other datasets so can combine by FIPS and years
  #2001 to 2002, 2006 to 2007, 2011 to 2012, and 2016 to 2017
  nlcd$Year[nlcd$Year==1996] <- 1997
  nlcd$Year[nlcd$Year==2001] <- 2002
  nlcd$Year[nlcd$Year==2006] <- 2007
  nlcd$Year[nlcd$Year==2011] <- 2012
  nlcd$Year[nlcd$Year==2016] <- 2017

#Write final nlcd data to be used in combination with other dataframes
  write_csv(nlcd, "Data/Future/DataProcessing/df/nlcd_5yrs.csv")
  
#Read in nlcd
nlcd<-read_csv("Data/Future/DataProcessing/df/nlcd_5yrs.csv")

#Read in other datasets from dataprocessing to create comparable fulldata_future dataset
    coa<-read_csv("Data/DataProcessing/df/coa.csv")
    cdl<-read_csv("Data/DataProcessing/df/cdl.csv")
    #Read in ERS file, to be combined with other data as is
    ERS<-readxl::read_xls("Data/DataProcessing/ERS/ERSRegions_To_Counties.xls")
    ERS<-ERS[,1:3]
    colnames(ERS)<-c("FIPS", "ERSCode", "ERSName")
    #Read in ASD file, to be combined with the other data as is
    ASD<-readr::read_csv("Data/DataProcessing/ASD/ASD_County_Crosswalk.csv") %>% 
      select(statecountyfips, StateASD)
    colnames(ASD)<-c("FIPS", "ASDCode")


#Make FIPS numeric for nlcd to match with other datasets
nlcd$FIPS<-as.numeric(nlcd$FIPS)
    
#Make fulldata_future
    #List and merge three datasets by the unique combination of FIPS and Year Values
fulldata<-list(coa, cdl, nlcd) %>% 
  reduce(full_join, by=c("FIPS", "Year"))

#Merge with ERS and ASD by just FIPS
fulldata<-list(fulldata, ERS, ASD) %>% 
  reduce(full_join, by=c("FIPS"))


#Drop the 9 VA counties 51515, 51530, 51580, 51595, 51600, 51610, 51678,51685, 51720 
  #that had NA in CDL and that are essentially within other counties
fulldata<-fulldata %>%
  filter(!(FIPS==51515)&!(FIPS==51530)&!(FIPS==51580)&!(FIPS==51595)&!(FIPS==51600)&
           !(FIPS==51610)&!(FIPS==51678)&!(FIPS==51685)&!(FIPS==51720))

#Use 2017 county area to fill all other year county area so standardized per FIPS
  fulldata<-fulldata %>% 
    dplyr::group_by(FIPS) %>% 
    arrange(desc(Year)) %>% 
    dplyr::mutate(countyarea=countyarea[1]) %>% 
    arrange(FIPS) %>% 
    dplyr::ungroup()

fulldata<-fulldata %>% 
  dplyr::mutate(cropintensity=harvcrop/((pland_crops/100)*countyarea)) %>% 
  dplyr::mutate(natural_crops_ed=tel_naturalcrops_nc/(countyarea*0.4046856422)) %>% #meters shared edge per hectare county area
  dplyr::mutate(forest_crops_ed=tel_forestcrop_fc/(countyarea*0.4046856422)) %>% 
  dplyr::mutate(shrubgrass_crops_ed=tel_shrubgrasscrop_sgc/(countyarea*0.4046856422))

#Replace infinite values with NA for regression 
  fulldata$cropintensity[sapply(fulldata$cropintensity, is.infinite)]<-NA
  fulldata$natural_crops_ed[sapply(fulldata$natural_crops_ed, is.infinite)]<-NA
  
#If harvcrop or pland_crops is 0 then make cropintensity 0 
  fulldata$cropintensity<- ifelse(fulldata$harvcrop==0, 0, fulldata$cropintensity)
  fulldata$cropintensity<- ifelse(fulldata$pland_crops==0, 0, fulldata$cropintensity)
  
#Remove rows with NA value for year
  fulldata<-fulldata[!is.na(fulldata$Year),]
  
#Name as fulldata_future
  fulldata_5yrs<-fulldata
    
#Write fulldata to df folder as all data pulled together
    write_csv(fulldata_5yrs, "Data/Future/DataProcessing/df/fulldata_5yrs.csv")
    save(fulldata_5yrs, file = "Data/Future/DataProcessing/df/fulldata_5yrs.rda")


###############################################
load("Data/Future/DataProcessing/df/fulldata_5yrs.rda")
#Load the needed packages (install first if necessary)
library(ggplot2) #data visualization
library(ggpubr)#To arrange ggplots on a page
library(stringr)#String detection
library(tidyverse) #Datatable manipulation (all functions)
library(dotwhisker) #relabel predictors
library(stargazer) #Create stargazer tables
library(clubSandwich) #For coeftest
#Perform different Models for Comparison
data_5yrs<-fulldata_5yrs %>% 
  select(FIPS, Year, ASDCode, ERSCode,
         insect_planted, pland_crops, harv_county, ed_crops, natural_crops_ed, mna_crops, largefarm_planted,
         soysmallgrain_planted, corn_planted, fruitveg_planted,pland_natural,
         msidi) %>% #Got rid of SDI for 5 years
  filter(harv_county>=0.01) %>% 
  na.omit() %>% 
    mutate(pland_c_n=pland_crops/pland_natural) %>% 
  mutate_at(scale, .vars=vars(-FIPS, -Year, -ERSCode, -ASDCode, -insect_planted)) %>%  #Scale by subtracting column mean and dividing by column SD
    rename(Insecticide=insect_planted,
         PercentCrop=pland_crops,
         HarvestedCrop=harv_county,
         CropEdge=ed_crops,
         NaturalCropEdge=natural_crops_ed,
         MeanCropArea=mna_crops,
         LargeFarms=largefarm_planted,
         SoyGrains=soysmallgrain_planted,
         Corn=corn_planted,
         FruitVeg=fruitveg_planted,
         LandDiversity=msidi)


lm_5yrs<-lm(Insecticide~PercentCrop+LargeFarms+
                  SoyGrains+Corn+FruitVeg+
                  factor(Year)+factor(ASDCode), data=data_5yrs)
car::vif(lm_5yrs) #NaturalCropEdge decreases VIF correlation by a lot, even if ed_crops had barely higher AIC/R2
summary(lm_5yrs)$r.squared
summary(lm_5yrs)$adj.r.squared
stats::AIC(lm_5yrs)
stats::nobs(lm_5yrs)

stargazer::stargazer(lm_5yrs, type="text", omit=c("ASDCode","Year"),
                     out="Data/Future/Visualize/test/test.txt",
                     omit.stat=c("LL","ser","f"))

```


