---
title: "Analyze"
author: "Sofie McComb"

output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This R Markdown document will perform the panel linear model regressions for determining the relationship of agricultural and landscape variables on insectide use in the present-day.

Twoways (individual and time) fixed effects models will be run for each regression. Individual will be represented by ASDCode and time will be represented by year.

 
## Data Preparation

This section will load the necessary packages and data

#### Load Packages

```{r packages, message=F, warning=F}

#Load the needed packages (install first if necessary)
library(tidyverse) #Datatable manipulation
library(purrr) #For reduce function using full_join
library(car) # For calculating variance inflation factors (vif)
library(broom) #Convert statistical analysis into df
library(reshape2)#For wide to long data format
library(clubSandwich) #for coeftest (cluster robust standard errors)

#Set options
options(scipen=999) #no scientific notation (all)

```


#### Load Data

Loading the fulldata dataset created in the DataProcessing.Rmd, which was developed to perform the regression analyses,
as well as fulldata_forecast for the forecasted versions of the 4 NLCD

```{r data, message=F, warning=F}

load("Data/DataProcessing/df/fulldata.rda")
load("Data/DataProcessing/Future/df/fulldata_forecast.rda")

```


## Panel Regression Analyses

###Model 1 
Census of Ag (Planted crop, large farms, crop covariates) for 4 years, all observations possible (no <1%)-all observations applies to all models

```{r}

data_model_1_na<-fulldata %>% 
  select(FIPS, Year, ASDCode, ERSCode,
         insect_planted, planted_county, largefarm_planted, 
         soysmallgrain_planted, corn_planted, fruitveg_planted,msidi,
         pland_crops, Prop_LCP) %>% #Included msidi, etc. so that 4 yrs of observations and same data rows as model 2
  na.omit() %>% #11405 observations %>% 
    select(FIPS, Year, ASDCode, ERSCode,
         insect_planted, planted_county, largefarm_planted, 
         soysmallgrain_planted, corn_planted, fruitveg_planted) 
dat1_fips<- data_model_1_na%>%
    group_by(FIPS) %>%
    summarise(count=n()) %>% 
  filter(count==4) %>% 
  select(FIPS) #Get FIPS FOR BALANCED PANEL
data_model_1<-left_join(dat1_fips, data_model_1_na)%>%#Balanced the panel, 10608 observations
  mutate_at(scale, .vars=vars(-FIPS, -Year, -ERSCode, -ASDCode, -insect_planted)) %>%  #Scale by subtracting column mean and dividing by column SD
    rename(Insecticide=insect_planted,
         PlantedCrop=planted_county,
         LargeFarms=largefarm_planted,
         SoyGrains=soysmallgrain_planted,
         Corn=corn_planted,
         FruitVeg=fruitveg_planted)

lm_model_1<-lm(Insecticide~PlantedCrop+LargeFarms+
                  SoyGrains+Corn+FruitVeg+
                  factor(Year)+factor(ASDCode), data=data_model_1)
df_coef_model_1<-lm_model_1 %>% 
  clubSandwich::coef_test(vcov = "CR2", cluster = data_model_1$ASDCode, test = "Satterthwaite")


```


###Model 2
Census of Ag (Planted crop, large farms, crop covariates) with naturalcropedge and land diversity for 4 years

```{r}

data_model_2_na<-fulldata %>% 
  select(FIPS, Year, ASDCode, ERSCode,
         insect_planted, planted_county, largefarm_planted, 
         soysmallgrain_planted, corn_planted, fruitveg_planted,
         natural_crops_ed, msidi,
         pland_crops, Prop_LCP) %>% 
  na.omit() %>% #11405 observations
    select(FIPS, Year, ASDCode, ERSCode,
         insect_planted, planted_county, largefarm_planted, 
         soysmallgrain_planted, corn_planted, fruitveg_planted,
         natural_crops_ed, msidi) 
dat2_fips<- data_model_2_na%>%
    group_by(FIPS) %>%
    summarise(count=n()) %>% 
  filter(count==4) %>% 
  select(FIPS) #Get FIPS FOR BALANCED PANEL
data_model_2<-left_join(dat2_fips, data_model_2_na)%>%#Balanced the panel, 10608 observations
  mutate_at(scale, .vars=vars(-FIPS, -Year, -ERSCode, -ASDCode, -insect_planted)) %>%  #Scale by subtracting column mean and dividing by column SD
    rename(Insecticide=insect_planted,
         PlantedCrop=planted_county,
         LargeFarms=largefarm_planted,
         SoyGrains=soysmallgrain_planted,
         Corn=corn_planted,
         FruitVeg=fruitveg_planted,
         NaturalCropEdge=natural_crops_ed,
         LandDiversity=msidi)

lm_model_2<-lm(Insecticide~PlantedCrop+LargeFarms+
                 SoyGrains+Corn+FruitVeg+
                 NaturalCropEdge+LandDiversity+
                 factor(Year)+factor(ASDCode), data=data_model_2)
df_coef_model_2<-lm_model_2 %>% 
  clubSandwich::coef_test(vcov = "CR2", cluster = data_model_2$ASDCode, test = "Satterthwaite")

```


###Model 3
Census of Ag (Planted crop, large farms, crop covariates) with natural cropedge and land diversity and crop diversity for only 3 years (no 2002)-only one with crop diversity

```{r}

data_model_3_na<-fulldata %>% 
  select(FIPS, Year, ASDCode, ERSCode,
         insect_planted, planted_county, largefarm_planted, 
         soysmallgrain_planted, corn_planted, fruitveg_planted,
         natural_crops_ed, msidi, SDI,pland_crops, Prop_LCP) %>% 
  na.omit() %>% #8578 observations
    select(FIPS, Year, ASDCode, ERSCode,
         insect_planted, planted_county, largefarm_planted, 
         soysmallgrain_planted, corn_planted, fruitveg_planted,
         natural_crops_ed, msidi, SDI) 
dat3_fips<- data_model_3_na%>%
    group_by(FIPS) %>%
    summarise(count=n()) %>% 
  filter(count==3) %>% 
  select(FIPS) #Get FIPS FOR BALANCED PANEL
data_model_3<-left_join(dat3_fips, data_model_3_na)%>%#Balanced the panel, 8178 observations
  mutate_at(scale, .vars=vars(-FIPS, -Year, -ERSCode, -ASDCode, -insect_planted)) %>%  #Scale by subtracting column mean and dividing by column SD
    rename(Insecticide=insect_planted,
         PlantedCrop=planted_county,
         LargeFarms=largefarm_planted,
         SoyGrains=soysmallgrain_planted,
         Corn=corn_planted,
         FruitVeg=fruitveg_planted,
         NaturalCropEdge=natural_crops_ed,
         LandDiversity=msidi,
         CropDiversity=SDI)

lm_model_3<-lm(Insecticide~PlantedCrop+LargeFarms+
                 SoyGrains+Corn+FruitVeg+
                 NaturalCropEdge+LandDiversity+ CropDiversity+
                 factor(Year)+factor(ASDCode), data=data_model_3)
df_coef_model_3<-lm_model_3 %>% 
  clubSandwich::coef_test(vcov = "CR2", cluster = data_model_3$ASDCode, test = "Satterthwaite")



```


###Model 4
NLCD equivalents (Percent cropland, LCP patch metric) with naturalcropedge and land diversity and crop covariates for 4 years (no large farms)

```{r}

data_model_4_na<-fulldata %>% 
  select(FIPS, Year, ASDCode, ERSCode,
         insect_planted, pland_crops, Prop_LCP, 
         soysmallgrain_planted, corn_planted, fruitveg_planted,
         natural_crops_ed, msidi, planted_county, largefarm_planted) %>% #Include planted_county and largefarm so exact same rows
  na.omit() %>% #11405 observations
   select(FIPS, Year, ASDCode, ERSCode,
         insect_planted, pland_crops, Prop_LCP, 
         soysmallgrain_planted, corn_planted, fruitveg_planted,
         natural_crops_ed, msidi) 
dat4_fips<- data_model_4_na%>%
    group_by(FIPS) %>%
    summarise(count=n()) %>% 
  filter(count==4) %>% 
  select(FIPS) #Get FIPS FOR BALANCED PANEL
data_model_4<-left_join(dat4_fips, data_model_4_na)%>%#Balanced the panel, 10608 observations
  mutate_at(scale, .vars=vars(-FIPS, -Year, -ERSCode, -ASDCode, -insect_planted)) %>%  #Scale by subtracting column mean and dividing by column SD
    rename(Insecticide=insect_planted,
         PercentCrop=pland_crops,
         LargeCropPatches=Prop_LCP,
         SoyGrains=soysmallgrain_planted,
         Corn=corn_planted,
         FruitVeg=fruitveg_planted,
         NaturalCropEdge=natural_crops_ed,
         LandDiversity=msidi)

lm_model_4<-lm(Insecticide~PercentCrop+LargeCropPatches+
                 SoyGrains+Corn+FruitVeg+
                 NaturalCropEdge+LandDiversity+
                 factor(Year)+factor(ASDCode), data=data_model_4)
df_coef_model_4<-lm_model_4 %>% 
  clubSandwich::coef_test(vcov = "CR2", cluster = data_model_4$ASDCode, test = "Satterthwaite")

```


###Model 5
Model 4 but without crop covariates

```{r}

data_model_5_na<-fulldata %>% 
  select(FIPS, Year, ASDCode, ERSCode,
         insect_planted, pland_crops, Prop_LCP, 
         soysmallgrain_planted, corn_planted, fruitveg_planted,
         natural_crops_ed, msidi, planted_county, largefarm_planted) %>% #Include planted_county and largefarm and crops so exact same rows
  na.omit() %>% #11405 observations
   select(FIPS, Year, ASDCode, ERSCode,
         insect_planted, pland_crops, Prop_LCP,
         natural_crops_ed, msidi) 
dat5_fips<- data_model_5_na%>%
    group_by(FIPS) %>%
    summarise(count=n()) %>% 
  filter(count==4) %>% 
  select(FIPS) #Get FIPS FOR BALANCED PANEL
data_model_5<-left_join(dat5_fips, data_model_5_na)%>%#Balanced the panel, 10608 observations
  mutate_at(scale, .vars=vars(-FIPS, -Year, -ERSCode, -ASDCode, -insect_planted)) %>%  #Scale by subtracting column mean and dividing by column SD
    rename(Insecticide=insect_planted,
         PercentCrop=pland_crops,
         LargeCropPatches=Prop_LCP,
         NaturalCropEdge=natural_crops_ed,
         LandDiversity=msidi)

lm_model_5<-lm(Insecticide~PercentCrop+LargeCropPatches+
                 NaturalCropEdge+LandDiversity+
                 factor(Year)+factor(ASDCode), data=data_model_5)
df_coef_model_5<-lm_model_5 %>% 
  clubSandwich::coef_test(vcov = "CR2", cluster = data_model_5$ASDCode, test = "Satterthwaite")

```


###Model 6
Modeled NLCD (forecast for 4 years for pcrop, patch metric, naturalcropedge, and diversity) with crop covariates


```{r}


data_model_6_na<-fulldata_forecast %>% 
  select(FIPS, Year, ASDCode, ERSCode,
         insect_planted, pland_crops, Prop_LCP, 
         soysmallgrain_planted, corn_planted, fruitveg_planted,
         natural_crops_ed, msidi, planted_county, largefarm_planted) %>% #Include planted_county and largefarm so exact same rows
  na.omit() %>% #11463 observations
   select(FIPS, Year, ASDCode, ERSCode,
         insect_planted, pland_crops, Prop_LCP, 
         soysmallgrain_planted, corn_planted, fruitveg_planted,
         natural_crops_ed, msidi) 
dat6_fips<- data_model_6_na%>%
    group_by(FIPS) %>%
    summarise(count=n()) %>% 
  filter(count==4) %>% 
  select(FIPS) #Get FIPS FOR BALANCED PANEL
data_model_6<-left_join(dat6_fips, data_model_6_na)%>%#Balanced the panel, 10660 observations
  mutate_at(scale, .vars=vars(-FIPS, -Year, -ERSCode, -ASDCode, -insect_planted)) %>%  #Scale by subtracting column mean and dividing by column SD
    rename(Insecticide=insect_planted,
         PercentCrop=pland_crops,
         LargeCropPatches=Prop_LCP,
         SoyGrains=soysmallgrain_planted,
         Corn=corn_planted,
         FruitVeg=fruitveg_planted,
         NaturalCropEdge=natural_crops_ed,
         LandDiversity=msidi)

lm_model_6<-lm(Insecticide~PercentCrop+LargeCropPatches+
                 SoyGrains+Corn+FruitVeg+
                 NaturalCropEdge+LandDiversity+
                 factor(Year)+factor(ASDCode), data=data_model_6)
df_coef_model_6<-lm_model_6 %>% 
  clubSandwich::coef_test(vcov = "CR2", cluster = data_model_6$ASDCode, test = "Satterthwaite")


```


###Model 7
Model 6 but without crop covariates

```{r}


data_model_7_na<-fulldata_forecast %>% 
  select(FIPS, Year, ASDCode, ERSCode,
         insect_planted, pland_crops, Prop_LCP, 
         soysmallgrain_planted, corn_planted, fruitveg_planted,
         natural_crops_ed, msidi, planted_county, largefarm_planted) %>% #Include planted_county and largefarm and crops so exact same rows
  na.omit() %>% #11463 observations
   select(FIPS, Year, ASDCode, ERSCode,
         insect_planted, pland_crops, Prop_LCP, 
         natural_crops_ed, msidi) 
dat7_fips<- data_model_7_na%>%
    group_by(FIPS) %>%
    summarise(count=n()) %>% 
  filter(count==4) %>% 
  select(FIPS) #Get FIPS FOR BALANCED PANEL
data_model_7<-left_join(dat7_fips, data_model_7_na)%>%#Balanced the panel, 10660 observations
  mutate_at(scale, .vars=vars(-FIPS, -Year, -ERSCode, -ASDCode, -insect_planted)) %>%  #Scale by subtracting column mean and dividing by column SD
    rename(Insecticide=insect_planted,
         PercentCrop=pland_crops,
         LargeCropPatches=Prop_LCP,
         NaturalCropEdge=natural_crops_ed,
         LandDiversity=msidi)

lm_model_7<-lm(Insecticide~PercentCrop+LargeCropPatches+
                 NaturalCropEdge+LandDiversity+
                 factor(Year)+factor(ASDCode), data=data_model_7)
df_coef_model_7<-lm_model_7 %>% 
  clubSandwich::coef_test(vcov = "CR2", cluster = data_model_7$ASDCode, test = "Satterthwaite")


```



###Table 1
Stargazer Table of 7 Models

```{r}


stargazer::stargazer(lm_model_1, lm_model_2, lm_model_3, lm_model_4,lm_model_5,lm_model_6,lm_model_7,
                     type="text", omit=c("ASDCode","Year"),
                     out="Data/Present/stargazer/7Models_stargazer_allplanted_balanced.txt",
                     omit.stat=c("LL","ser","f"),
                     se = list(df_coef_model_1[,2],df_coef_model_2[,2],df_coef_model_3[,2],df_coef_model_4[,2],df_coef_model_5[,2],
                               df_coef_model_6[,2],df_coef_model_7[,2]),
                     p=list(df_coef_model_1[,5],df_coef_model_2[,5],df_coef_model_3[,5],df_coef_model_4[,5],df_coef_model_5[,5],
                            df_coef_model_6[,5],df_coef_model_7[,5]))


```


### Table 2
Statistics: #Obs, Adjusted R2, AIC, BIC

```{r}

calc_model_stats<-function(modelname){
  modelnm<-modelname
  statsdf<-as.data.frame(cbind(nobs(modelnm),
                 summary(modelnm)$adj.r.squared,
                 stats::AIC(modelnm),
                 stats::BIC(modelnm)))
  return(statsdf)
}

#Calc stats for each model
stats_model_1<-calc_model_stats(lm_model_1)
stats_model_2<-calc_model_stats(lm_model_2)
stats_model_3<-calc_model_stats(lm_model_3)
stats_model_4<-calc_model_stats(lm_model_4)
stats_model_5<-calc_model_stats(lm_model_5)
stats_model_6<-calc_model_stats(lm_model_6)
stats_model_7<-calc_model_stats(lm_model_7)

#Rbind together
stats_model<-rbind(stats_model_1, stats_model_2, stats_model_3, stats_model_4, stats_model_5,
                   stats_model_6,stats_model_7) %>% 
  mutate(Model=1:7) %>% 
  select(Model, everything())
colnames(stats_model)<-c("Model", "Observations", "Adjusted R2", "AIC", "BIC")
stats_model

```


###VIF Tables

```{r}

calc_vif<-function(modelname){
  modelnm<-modelname
  vif_df<-rownames_to_column(as.data.frame(car::vif(modelnm))) %>% 
    select(1, 4)
  colnames(vif_df)<-c("Variable", "VIF")
  return(vif_df)
}

vif_model_1<-calc_vif(lm_model_1) %>% rename(Model1=VIF)
vif_model_2<-calc_vif(lm_model_2) %>% rename(Model2=VIF)
vif_model_3<-calc_vif(lm_model_3) %>% rename(Model3=VIF)
vif_model_4<-calc_vif(lm_model_4) %>% rename(Model4=VIF)
vif_model_5<-calc_vif(lm_model_5) %>% rename(Model5=VIF)
vif_model_6<-calc_vif(lm_model_6) %>% rename(Model6=VIF)
vif_model_7<-calc_vif(lm_model_7) %>% rename(Model7=VIF)

vif_model<-list(vif_model_1, vif_model_2, vif_model_3, vif_model_4,vif_model_5,vif_model_6,vif_model_7) %>% 
  reduce(full_join, by="Variable")
vif_model


```


