---
title: "Analysis"
author: "Sofie McComb"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This R Markdown document will ...

The regression combinations I need:

Write out all the options 
Fraction Crop (Area)=pland_crops
Crop Intensity (harv ac/area crop (NLCD*CoA))=cropintensity
Crop diversity=SDI
Landscape diversity=msidi
Edge Natural habitat-crop=te_shared_c_nc
Patch size of cropland= mna_crops
Large Farms (Acreage harv acres to farms >500acres)=largefarm_planted


+crop covariates (fruits, veg, etc)=soysmallgrain_planted + corn_planted + fruitveg_planted
+county, year FES
Run for all counties pooled and Run for ERS regions
Possible additional: income_planted  + irrigate_planted

Model ignoring CDL as well to have all the years

The other regression column desired is shared edge length between natural and cropland (which is tel_naturalcrops_nc) divided by the total edge length of crop (tec_crops_nc), which is already a created column called te_shared_c_nc


## Data Formatting

```{r packages, message=F, warning=F}

# #Load the needed packages, which are loaded in the R scrips as well (install first if necessary)
library(tidyverse) #Datatable manipulation (all functions)
library(tools) #For file_path sans_ext (COA.R)
library(purrr) #For reduce function using full_join (COA.R)
library(zoo) #For na.locf function (COA.R)
library(janitor) #Clean colnames (CDL.R)
library(vegan) #Perform diversity calculation (CDL.R)
library(readxl) #read excel .xlsx (ERS data)
library(ggplot2) #data visualization
library(stargazer)#regression and summary statistics tables
library(plm) #linear models for panel data
library(lmtest) #testing for linear regression models


# 
#Set options
options(scipen=999) #no scientific notation (all)



```




### Panel Fixed effects lm

Helpful websites: https://rstudio-pubs-static.s3.amazonaws.com/372492_3e05f38dd3f248e89cdedd317d603b9a.html 
https://cran.r-project.org/web/packages/plm/vignettes/plmPackage.html


Versions of regression:
1. All counties pooled (twoways, individual, time)
  a. All 7 variables (use var7)
  b. 6 variables (no CDL) (use var6)
  c. 6 variables (no CDL)-but just 3 years that have CDL (not 1997/2002) (use var6 on subset data)
  d. With all crop covariates
  e. Future choices: other variable combinations or just one variable each
2. ERS Regions
  *Same as above but substetted by regions

## Source Data and Code

```{r source, message=F, warning=F}

source("R/run_plm.R")
load("Data/df/fulldata.rda")

```

#### PLM Function 
  run_plm<-function(predictors,
                    data=fulldata,index = c("FIPS","Year"), model = "within",effect = "twoways"){
    Formula=as.formula(paste("insect_planted ~ ", paste(predictors, collapse=" + ")))
    plm_model<-plm(Formula, 
                   data = data,
                   index = index,
                   model = model,
                   effect = effect)
    return(plm_model)
  }

### Establish Model Inputs

```{r model inputs, message=F, warning=F}

#Create Variable Combinations
var7<-c("pland_crops","cropintensity", "msidi","mna_crops","largefarm_planted","te_shared_c_nc","SDI")
var6<-c("pland_crops","cropintensity", "msidi","mna_crops","largefarm_planted","te_shared_c_nc")
var7crops<-c("pland_crops","cropintensity", "msidi","mna_crops","largefarm_planted","te_shared_c_nc","SDI",
             "soysmallgrain_planted", "corn_planted", "fruitveg_planted")
var6crops<-c("pland_crops","cropintensity", "msidi","mna_crops","largefarm_planted","te_shared_c_nc",
             "soysmallgrain_planted", "corn_planted", "fruitveg_planted")

#Data subset that has 1997 and 2002 removed, since there are so many NAs for those years across the datasets
fulldata_3yrs<-fulldata[fulldata$Year!=1997&fulldata$Year!=2002,]

```


Creating subsets of fulldata to be used to run regressions on specific subsets of the data.???
Instead for ERS or other subsets just create a forloop in that section that subsets the fulldata
by a set iteration (such as the 9 ERS numbers) and then saves the model by that iteration number


## Run Regressions
Call the name of the model when run the name of the model saved. Whenever it will be loaded back, it will be loaded to that exact same name.

### 1) Counties Pooled (cp)

Eventually made put this in a separate script and source it
#Create list of models and save that as as RDA

```{r pooled, message=F, warning=F}
#For each option perform: twoways, individual, and time fixed effects

#A) All 7 variables
cp_twoways_var7<-run_plm(predictors=var7)
cp_individual_var7<-run_plm(predictors=var7, effect = "individual")
cp_time_var7<-run_plm(predictors=var7, effect = "time")

#B) 6 variables (no CDL)
cp_twoways_var6<-run_plm(predictors=var6)
cp_individual_var6<-run_plm(predictors=var6, effect = "individual")
cp_time_var6<-run_plm(predictors=var6, effect = "time")

#C) 6 variables (no CDL) but only 2007, 2012, and 2017 to match 3 years with CDL
cp_twoways_var6_3yrs<-run_plm(predictors=var6, data=fulldata_3yrs)
cp_individual_var6_3yrs<-run_plm(predictors=var6, effect = "individual", data=fulldata_3yrs)
cp_time_var6_3yrs<-run_plm(predictors=var6, effect = "time", data=fulldata_3yrs)

#D) All crops covariates, repeating A-C with these inclusions
#var7crops
cp_twoways_var7crops<-run_plm(predictors=var7crops)
cp_individual_var7crops<-run_plm(predictors=var7crops, effect = "individual")
cp_time_var7crops<-run_plm(predictors=var7crops, effect = "time")

#var6crops
cp_twoways_var6crops<-run_plm(predictors=var6crops)
cp_individual_var6crops<-run_plm(predictors=var6crops, effect = "individual")
cp_time_var6crops<-run_plm(predictors=var6crops, effect = "time")

#var6crops with fulldata_3yrs
cp_twoways_var6crops_3yrs<-run_plm(predictors=var6crops, data=fulldata_3yrs)
cp_individual_var6crops_3yrs<-run_plm(predictors=var6crops, effect = "individual", data=fulldata_3yrs)
cp_time_var6crops_3yrs<-run_plm(predictors=var6crops, effect = "time", data=fulldata_3yrs)

models<-list(cp_twoways_var7,cp_individual_var7,cp_time_var7)
save(models, file = paste0("Data/models/models"))



```



### 2) By ERS Region


```{r}


#variables <- c("harv_county", "SDI")
variables<-c("pland_crops","cropintensity","SDI", "msidi","mna_crops","largefarm_planted","te_shared_c_nc")
#Could make a whole bunch of versions and then apply the function to the list of variable lists, and then combine the results

modelnm<-run_plm(predictors=variables)
save(modelnm, file = paste0("Data/models/testing.rda"))

#Instead of stargazer maybe just save rda of each model
#And later go through whole folder, pull them in, and put info from them in compiled text pdf
#And then maybe csv


```


#Potential possibility of extracting information from heach model and running it
#Could list the models?

An object of class c("plm", "panelmodel").

A "plm" object has the following elements :

coefficients: the vector of coefficients,
vcov: the variance–covariance matrix of the coefficients,
residuals: the vector of residuals (these are the residuals of the (quasi-)demeaned model),
weights: (only for weighted estimations) weights as specified,
df.residual: degrees of freedom of the residuals,
formula	: an object of class "pFormula" describing the model,
model	: the model frame as a "pdata.frame" containing the variables used for estimation: the response is in first column followed by the other variables, the individual and time indexes are in the 'index' attribute of model,
ercomp	: an object of class "ercomp" providing the estimation of the components of the errors (for random effects models only),
aliased	: named logical vector indicating any aliased coefficients which are silently dropped by plm due to linearly dependent terms (see also detect.lindep),
call	:the call.


```{r}

myFun <-
function(plm)
{
out <- c(plm$coefficients[1],
	lm$coefficients[2],
	length(lm$model$y),
	summary(lm)$coefficients[2,2],
	pf(summary(lm)$fstatistic[1], summary(lm)$fstatistic[2],
summary(lm)$fstatistic[3], lower.tail = FALSE),
	summary(lm)$r.squared)
names(out) <- c("intercept","slope","n","slope.SE","p.value","r.squared")
return(out)}


#Edit above on the list of models

#Plm object has the follwing elements
#want to save and report the coefficients,

#vcov is cool but har to include in csv table

cp_var7$coefficients
cp_var7$vcov



```

