---
title: "Analysis"
author: "Sofie McComb"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This R Markdown document will perform the panel linear model regressions for determining the relationship of agricultural and landscape variables on insectide use.

Twoways (individual and time) fixed effects models will be run for each regression. Individual will be represented by ASDCode and time will be represented by year.

Using broom package to put plm model informatino into tidy dataframe format. 
For more information: https://cran.r-project.org/web/packages/broom/vignettes/broom.html

Using clubsandwih package to perform cluster-robust standard errors in tidy format.
For more information: https://cran.r-project.org/web/packages/clubSandwich/vignettes/panel-data-CRVE.html

Using car::vif to run variance  variance inflation factor (vif) to look at multicollinearity between variables 
(VIF of 1=no correlation among predictors, >4 investigate, >10 serious correction)

 
## Data Preparation

This section will load the necessary packages and data

#### Load Packages

```{r packages, message=F, warning=F}

#Load the needed packages (install first if necessary)
library(tidyverse) #Datatable manipulation
library(purrr) #For reduce function using full_join
library(car) # For calculating variance inflation factors (vif)
library(broom) #Convert statistical analysis into df
library(reshape2)#For wide to long data format
library(clubSandwich) #for coeftest (cluster robust standard errors)

#Set options
options(scipen=999) #no scientific notation (all)

```


#### Load Data

Loading the fulldata dataset created in the DataProcessing.Rmd, which was developed to perform the regression analyses.

```{r data, message=F, warning=F}

load("Data/DataProcessing/df/fulldata.rda")

```


## Panel Regression Analyses

### Landscape composition and configuration
Variables: Percent crop, edge density crops, mean patch size crops, large farms, 3 crop covariates
4 models total with counties pooled to account for crops vs no crops, and 4 yrs vs 3 years of data

  pland_crops=Percentage of county with cropland area, in percent 
  ed_crops=edge density of crops, in meters/hectares
  mna_crops= Mean patch size of cropland, in hectares
  largefarm_planted= Acreage of harvested acres for farms >500acres divided by acreage planted cropland, in acres/acres 
  
  Crop covariates:
  soysmallgrain_planted= acreage of soy/small grain divided by acreage planted cropland, in acres/acres
  corn_planted=acreage of corn divided by acreage planted cropland, in acres/acres
  fruitveg_planted=acreage of fruit and vegetables divided by acreage planted cropland, in acres/acres



```{r}

#Models examining landscape composition and configuration
#Model 1: no crops, 4 years of data: nocrops_4yrs
#Model 2: no crops, 3 years of data: nocrop_3yrs
#Model 3: crops, 4 years of data: crops_4yrs
#Model 4: crops, 3 years of data: crops_3yrs

###############################################
#Model1: nocrops_4yrs
data_nocrops_4yrs<-fulldata %>% 
  select(FIPS, Year, ASDCode, ERSCode,
         insect_planted, pland_crops, ed_crops, mna_crops, largefarm_planted) %>% 
  na.omit() %>% #11989 observations
  mutate_at(scale, .vars=vars(-FIPS, -Year, -ERSCode, -ASDCode, -insect_planted)) %>%  #Scale by subtracting column mean and dividing by column SD
    rename(Insecticide=insect_planted,
         PercentCrop=pland_crops,
         CropEdge=ed_crops,
         MeanCropArea=mna_crops,
         LargeFarms=largefarm_planted)
save(data_nocrops_4yrs, file="Data/Analysis/models/df/data_nocrops_4yrs.Rda")

lm_nocrops_4yrs<-lm(Insecticide~PercentCrop+CropEdge+MeanCropArea+LargeFarms+factor(Year)+factor(ASDCode), data=data_nocrops_4yrs)
save(lm_nocrops_4yrs, file="Data/Analysis/models/lm_nocrops_4yrs.Rda")
df_nocrops_4yrs<-broom::tidy(lm_nocrops_4yrs) %>% 
  mutate(model="nocrops_4yrs") %>% 
  dplyr::filter(!stringr::str_detect(term, "(Intercept)"),
                !stringr::str_detect(term, "factor"))
df_coef_nocrops_4yrs<-lm_nocrops_4yrs %>% 
  clubSandwich::coef_test(vcov = "CR2", cluster = data_nocrops_4yrs$ASDCode, test = "Satterthwaite") %>% 
  tibble::rownames_to_column(var = "term") %>% 
  rename(estimate=beta, std.error=SE, statistic=tstat, p.value=p_Satt) %>% 
  dplyr::mutate(model="nocrops_4yrs") %>% 
  dplyr::filter(!stringr::str_detect(term, "(Intercept)"),
                !stringr::str_detect(term, "factor"))
vif_nocrops_4yrs<-rownames_to_column(as.data.frame(car::vif(lm_nocrops_4yrs)), "term") %>% 
    dplyr::mutate(model="nocrops_4yrs")
###############################################


###############################################
#Model2: nocrops_3yrs
data_nocrops_3yrs<-fulldata %>% 
  select(FIPS, Year, ASDCode, ERSCode,
         insect_planted, pland_crops, ed_crops, mna_crops, largefarm_planted) %>% 
  filter(!Year==2002)%>% #Only 3 years of data, to later match with crop diversity
  na.omit() %>% #8984 observations
  mutate_at(scale, .vars=vars(-FIPS, -Year, -ERSCode, -ASDCode, -insect_planted)) %>%  #Scale by subtracting column mean and dividing by column SD
    rename(Insecticide=insect_planted,
         PercentCrop=pland_crops,
         CropEdge=ed_crops,
         MeanCropArea=mna_crops,
         LargeFarms=largefarm_planted)
save(data_nocrops_3yrs, file="Data/Analysis/models/df/data_nocrops_3yrs.Rda")

lm_nocrops_3yrs<-lm(Insecticide~PercentCrop+CropEdge+MeanCropArea+LargeFarms+factor(Year)+factor(ASDCode), data=data_nocrops_3yrs)
save(lm_nocrops_3yrs, file="Data/Analysis/models/lm_nocrops_3yrs.Rda")
df_nocrops_3yrs<-broom::tidy(lm_nocrops_3yrs) %>% 
  mutate(model="nocrops_3yrs") %>% 
  dplyr::filter(!stringr::str_detect(term, "(Intercept)"),
                !stringr::str_detect(term, "factor"))
df_coef_nocrops_3yrs<-lm_nocrops_3yrs %>% 
  clubSandwich::coef_test(vcov = "CR2", cluster = data_nocrops_3yrs$ASDCode, test = "Satterthwaite") %>% 
  tibble::rownames_to_column(var = "term") %>% 
  rename(estimate=beta, std.error=SE, statistic=tstat, p.value=p_Satt) %>% 
  dplyr::mutate(model="nocrops_3yrs") %>% 
  dplyr::filter(!stringr::str_detect(term, "(Intercept)"),
                !stringr::str_detect(term, "factor"))
vif_nocrops_3yrs<-rownames_to_column(as.data.frame(car::vif(lm_nocrops_3yrs)), "term") %>% 
    dplyr::mutate(model="nocrops_3yrs")
###############################################


###############################################
#Model3: crops_4yrs
data_crops_4yrs<-fulldata %>% 
  select(FIPS, Year, ASDCode, ERSCode,
         insect_planted, pland_crops, ed_crops, mna_crops, largefarm_planted,
         soysmallgrain_planted, corn_planted, fruitveg_planted) %>% 
  na.omit() %>% #11924 observations
  mutate_at(scale, .vars=vars(-FIPS, -Year, -ERSCode, -ASDCode, -insect_planted)) %>%  #Scale by subtracting column mean and dividing by column SD
    rename(Insecticide=insect_planted,
         PercentCrop=pland_crops,
         CropEdge=ed_crops,
         MeanCropArea=mna_crops,
         LargeFarms=largefarm_planted,
         SoyGrains=soysmallgrain_planted,
         Corn=corn_planted,
         FruitVeg=fruitveg_planted)
save(data_crops_4yrs, file="Data/Analysis/models/df/data_crops_4yrs.Rda")

lm_crops_4yrs<-lm(Insecticide~PercentCrop+CropEdge+MeanCropArea+LargeFarms+
                    SoyGrains+Corn+FruitVeg+factor(Year)+factor(ASDCode), data=data_crops_4yrs)
save(lm_crops_4yrs, file="Data/Analysis/models/lm_crops_4yrs.Rda")
df_crops_4yrs<-broom::tidy(lm_crops_4yrs) %>% 
  mutate(model="crops_4yrs") %>% 
  dplyr::filter(!stringr::str_detect(term, "(Intercept)"),
                !stringr::str_detect(term, "factor"))
df_coef_crops_4yrs<-lm_crops_4yrs %>% 
  clubSandwich::coef_test(vcov = "CR2", cluster = data_crops_4yrs$ASDCode, test = "Satterthwaite") %>% 
  tibble::rownames_to_column(var = "term") %>% 
  rename(estimate=beta, std.error=SE, statistic=tstat, p.value=p_Satt) %>% 
  dplyr::mutate(model="crops_4yrs") %>% 
  dplyr::filter(!stringr::str_detect(term, "(Intercept)"),
                !stringr::str_detect(term, "factor"))
vif_crops_4yrs<-rownames_to_column(as.data.frame(car::vif(lm_crops_4yrs)), "term") %>% 
    dplyr::mutate(model="crops_4yrs")
###############################################


###############################################
#Model4: crops_3yrs
data_crops_3yrs<-fulldata %>% 
  select(FIPS, Year, ASDCode, ERSCode,
         insect_planted, pland_crops, ed_crops, mna_crops, largefarm_planted,
         soysmallgrain_planted, corn_planted, fruitveg_planted) %>% 
    filter(!Year==2002)%>% #Only 3 years of data, to later match with crop diversity
  na.omit() %>% #8939 observations
  mutate_at(scale, .vars=vars(-FIPS, -Year, -ERSCode, -ASDCode, -insect_planted)) %>%  #Scale by subtracting column mean and dividing by column SD
    rename(Insecticide=insect_planted,
         PercentCrop=pland_crops,
         CropEdge=ed_crops,
         MeanCropArea=mna_crops,
         LargeFarms=largefarm_planted,
         SoyGrains=soysmallgrain_planted,
         Corn=corn_planted,
         FruitVeg=fruitveg_planted)
save(data_crops_3yrs, file="Data/Analysis/models/df/data_crops_3yrs.Rda")

lm_crops_3yrs<-lm(Insecticide~PercentCrop+CropEdge+MeanCropArea+LargeFarms+
                    SoyGrains+Corn+FruitVeg+factor(Year)+factor(ASDCode), data=data_crops_3yrs)
save(lm_crops_3yrs, file="Data/Analysis/models/lm_crops_3yrs.Rda")
df_crops_3yrs<-broom::tidy(lm_crops_3yrs) %>% 
  mutate(model="crops_3yrs") %>% 
  dplyr::filter(!stringr::str_detect(term, "(Intercept)"),
                !stringr::str_detect(term, "factor"))
df_coef_crops_3yrs<-lm_crops_3yrs %>% 
  clubSandwich::coef_test(vcov = "CR2", cluster = data_crops_3yrs$ASDCode, test = "Satterthwaite") %>% 
  tibble::rownames_to_column(var = "term") %>% 
  rename(estimate=beta, std.error=SE, statistic=tstat, p.value=p_Satt) %>% 
  dplyr::mutate(model="crops_3yrs") %>% 
  dplyr::filter(!stringr::str_detect(term, "(Intercept)"),
                !stringr::str_detect(term, "factor"))
vif_crops_3yrs<-rownames_to_column(as.data.frame(car::vif(lm_crops_3yrs)), "term") %>% 
    dplyr::mutate(model="crops_3yrs")
###############################################


#Combine and save the models
basemodels_df<-rbind(df_nocrops_4yrs, df_nocrops_3yrs, df_crops_4yrs, df_crops_3yrs)
basemodels_df_coef<-rbind(df_coef_nocrops_4yrs, df_coef_nocrops_3yrs, df_coef_crops_4yrs, df_coef_crops_3yrs)
basemodels_vif<-rbind(vif_nocrops_4yrs, vif_nocrops_3yrs, vif_crops_4yrs, vif_crops_3yrs)

#Write csv for each of the created dataframes
write_csv(basemodels_df, "Data/Analysis/df/basemodels_df.csv")
write_csv(basemodels_df_coef, "Data/Analysis/df/basemodels_df_coef.csv")
write_csv(basemodels_vif, "Data/Analysis/df/basemodels_vif.csv")



```


### Diversity
Add in landscape diversity and crop diversity to crops_3yrs model from previous step

  SDI=Simpson's Crop diversity, 0-1 value
  msidi=Simpson's landscape diversity, 0-1 value 


```{r}

#Similar to crops_3yrs, but adding diversity
data_diversity<-fulldata %>% 
  select(FIPS, Year, ASDCode, ERSCode,
         insect_planted, pland_crops, ed_crops, mna_crops, largefarm_planted,
         soysmallgrain_planted, corn_planted, fruitveg_planted,
         msidi, SDI) %>% 
    filter(!Year==2002)%>% #Only 3 years of data
  na.omit() %>% #8939 observations (match crops_3yrs)
  mutate_at(scale, .vars=vars(-FIPS, -Year, -ERSCode, -ASDCode, -insect_planted)) %>%  #Scale by subtracting column mean and dividing by column SD
    rename(Insecticide=insect_planted,
         PercentCrop=pland_crops,
         CropEdge=ed_crops,
         MeanCropArea=mna_crops,
         LargeFarms=largefarm_planted,
         SoyGrains=soysmallgrain_planted,
         Corn=corn_planted,
         FruitVeg=fruitveg_planted,
         LandDiversity=msidi,
         CropDiversity=SDI)
save(data_diversity, file="Data/Analysis/models/df/data_diversity.Rda")

lm_diversity<-lm(Insecticide~PercentCrop+CropEdge+MeanCropArea+LargeFarms+
                  SoyGrains+Corn+FruitVeg+LandDiversity+CropDiversity+
                  factor(Year)+factor(ASDCode), data=data_diversity)
save(lm_diversity, file="Data/Analysis/models/lm_diversity.Rda")
df_diversity<-broom::tidy(lm_diversity) %>% 
  mutate(model="diversity") %>% 
  dplyr::filter(!stringr::str_detect(term, "(Intercept)"),
                !stringr::str_detect(term, "factor"))
df_coef_diversity<-lm_diversity %>% 
  clubSandwich::coef_test(vcov = "CR2", cluster = data_diversity$ASDCode, test = "Satterthwaite") %>% 
  tibble::rownames_to_column(var = "term") %>% 
  rename(estimate=beta, std.error=SE, statistic=tstat, p.value=p_Satt) %>% 
  dplyr::mutate(model="diversity") %>% 
  dplyr::filter(!stringr::str_detect(term, "(Intercept)"),
                !stringr::str_detect(term, "factor"))
vif_diversity<-rownames_to_column(as.data.frame(car::vif(lm_diversity)), "term") %>% 
    mutate(model="diversity")

#Write csv for each of the created dataframes
write_csv(df_diversity, "Data/Analysis/df/df_diversity.csv")
write_csv(df_coef_diversity, "Data/Analysis/df/df_coef_diversity.csv") 
write_csv(vif_diversity, "Data/Analysis/df/vif_diversity.csv")


```



### Edge Density Interactions
Replace crop edge with specific edge types (natural-crop edge, forest-crop edge shrubgrass-crop edge) to examine how results change based on edge interactions

  natural_crops_ed= Shared edge length between natural land and cropland divided by the total county area, in meters/hectares [edge density]
  forest_crops_ed= Shared edge length between forest land and cropland divided by the total county area, in meters/hectares [edge density]
  shrubgrass_crops_ed= Shared edge length between shrubgrass land and cropland divided by the total county area, in meters/hectares [edge     density]

```{r}

###############################################
#Edge 1: Natural-Crop Edge
data_natural<-fulldata %>% 
  select(FIPS, Year, ASDCode, ERSCode,
         insect_planted, pland_crops, natural_crops_ed, mna_crops, largefarm_planted,
         soysmallgrain_planted, corn_planted, fruitveg_planted,
         msidi, SDI) %>% 
    filter(!Year==2002)%>% #Only 3 years of data
  na.omit() %>% #8939 observations (match crops_3yrs and diversity)
  mutate_at(scale, .vars=vars(-FIPS, -Year, -ERSCode, -ASDCode, -insect_planted)) %>%  #Scale by subtracting column mean and dividing by column SD
    rename(Insecticide=insect_planted,
         PercentCrop=pland_crops,
         NaturalCropEdge=natural_crops_ed,
         MeanCropArea=mna_crops,
         LargeFarms=largefarm_planted,
         SoyGrains=soysmallgrain_planted,
         Corn=corn_planted,
         FruitVeg=fruitveg_planted,
         LandDiversity=msidi,
         CropDiversity=SDI)
save(data_natural, file="Data/Analysis/models/df/data_natural.Rda")

lm_natural<-lm(Insecticide~PercentCrop+NaturalCropEdge+MeanCropArea+LargeFarms+
                  SoyGrains+Corn+FruitVeg+LandDiversity+CropDiversity+
                  factor(Year)+factor(ASDCode), data=data_natural)
save(lm_natural, file="Data/Analysis/models/lm_natural.Rda")
df_natural<-broom::tidy(lm_natural) %>% 
  mutate(model="natural") %>% 
  dplyr::filter(!stringr::str_detect(term, "(Intercept)"),
                !stringr::str_detect(term, "factor"))
df_coef_natural<-lm_natural %>% 
  clubSandwich::coef_test(vcov = "CR2", cluster = data_natural$ASDCode, test = "Satterthwaite") %>% 
  tibble::rownames_to_column(var = "term") %>% 
  rename(estimate=beta, std.error=SE, statistic=tstat, p.value=p_Satt) %>% 
  dplyr::mutate(model="natural") %>% 
  dplyr::filter(!stringr::str_detect(term, "(Intercept)"),
                !stringr::str_detect(term, "factor"))
vif_natural<-rownames_to_column(as.data.frame(car::vif(lm_natural)), "term") %>% 
    dplyr::mutate(model="natural")
###############################################

###############################################
#Edge 2: Forest-Crop Edge
data_forest<-fulldata %>% 
  select(FIPS, Year, ASDCode, ERSCode,
         insect_planted, pland_crops, forest_crops_ed, mna_crops, largefarm_planted,
         soysmallgrain_planted, corn_planted, fruitveg_planted,
         msidi, SDI) %>% 
    filter(!Year==2002)%>% #Only 3 years of data
  na.omit() %>% #8939 observations (match crops_3yrs and diversity)
  mutate_at(scale, .vars=vars(-FIPS, -Year, -ERSCode, -ASDCode, -insect_planted)) %>%  #Scale by subtracting column mean and dividing by column SD
    rename(Insecticide=insect_planted,
         PercentCrop=pland_crops,
         ForestCropEdge=forest_crops_ed,
         MeanCropArea=mna_crops,
         LargeFarms=largefarm_planted,
         SoyGrains=soysmallgrain_planted,
         Corn=corn_planted,
         FruitVeg=fruitveg_planted,
         LandDiversity=msidi,
         CropDiversity=SDI)
save(data_forest, file="Data/Analysis/models/df/data_forest.Rda")

lm_forest<-lm(Insecticide~PercentCrop+ForestCropEdge+MeanCropArea+LargeFarms+
                  SoyGrains+Corn+FruitVeg+LandDiversity+CropDiversity+
                  factor(Year)+factor(ASDCode), data=data_forest)
save(lm_forest, file="Data/Analysis/models/lm_forest.Rda")
df_forest<-broom::tidy(lm_forest) %>% 
  mutate(model="forest") %>% 
  dplyr::filter(!stringr::str_detect(term, "(Intercept)"),
                !stringr::str_detect(term, "factor"))
df_coef_forest<-lm_forest %>% 
  clubSandwich::coef_test(vcov = "CR2", cluster = data_forest$ASDCode, test = "Satterthwaite") %>% 
  tibble::rownames_to_column(var = "term") %>% 
  rename(estimate=beta, std.error=SE, statistic=tstat, p.value=p_Satt) %>% 
  dplyr::mutate(model="forest") %>% 
  dplyr::filter(!stringr::str_detect(term, "(Intercept)"),
                !stringr::str_detect(term, "factor"))
vif_forest<-rownames_to_column(as.data.frame(car::vif(lm_forest)), "term") %>% 
    mutate(model="forest")
###############################################

###############################################
#Edge 3: Shrubgrass-Crop Edge
data_shrubgrass<-fulldata %>% 
  select(FIPS, Year, ASDCode, ERSCode,
         insect_planted, pland_crops, shrubgrass_crops_ed, mna_crops, largefarm_planted,
         soysmallgrain_planted, corn_planted, fruitveg_planted,
         msidi, SDI) %>% 
    filter(!Year==2002)%>% #Only 3 years of data
  na.omit() %>% #8939 observations (match crops_3yrs and diversity)
  mutate_at(scale, .vars=vars(-FIPS, -Year, -ERSCode, -ASDCode, -insect_planted)) %>%  #Scale by subtracting column mean and dividing by column SD
    rename(Insecticide=insect_planted,
         PercentCrop=pland_crops,
         ShrubgrassCropEdge=shrubgrass_crops_ed,
         MeanCropArea=mna_crops,
         LargeFarms=largefarm_planted,
         SoyGrains=soysmallgrain_planted,
         Corn=corn_planted,
         FruitVeg=fruitveg_planted,
         LandDiversity=msidi,
         CropDiversity=SDI)
save(data_shrubgrass, file="Data/Analysis/models/df/data_shrubgrass.Rda")

lm_shrubgrass<-lm(Insecticide~PercentCrop+ShrubgrassCropEdge+MeanCropArea+LargeFarms+
                  SoyGrains+Corn+FruitVeg+LandDiversity+CropDiversity+
                  factor(Year)+factor(ASDCode), data=data_shrubgrass)
save(lm_shrubgrass, file="Data/Analysis/models/lm_shrubgrass.Rda")
df_shrubgrass<-broom::tidy(lm_shrubgrass) %>% 
  mutate(model="shrubgrass") %>% 
  dplyr::filter(!stringr::str_detect(term, "(Intercept)"),
                !stringr::str_detect(term, "factor"))
df_coef_shrubgrass<-lm_shrubgrass %>% 
  clubSandwich::coef_test(vcov = "CR2", cluster = data_shrubgrass$ASDCode, test = "Satterthwaite") %>% 
  tibble::rownames_to_column(var = "term") %>% 
  rename(estimate=beta, std.error=SE, statistic=tstat, p.value=p_Satt) %>% 
  dplyr::mutate(model="shrubgrass") %>% 
  dplyr::filter(!stringr::str_detect(term, "(Intercept)"),
                !stringr::str_detect(term, "factor"))
vif_shrubgrass<-rownames_to_column(as.data.frame(car::vif(lm_shrubgrass)), "term") %>% 
    mutate(model="shrubgrass")
###############################################


#Combine and save the models
edgemodels_df<-rbind(df_natural, df_forest, df_shrubgrass)
edgemodels_df_coef<-rbind(df_coef_natural, df_coef_forest, df_coef_shrubgrass)
edgemodels_vif<-rbind(vif_natural, vif_forest, vif_shrubgrass)

#Write csv for each of the created dataframes
write_csv(edgemodels_df, "Data/Analysis/df/edgemodels_df.csv")
write_csv(edgemodels_df_coef, "Data/Analysis/df/edgemodels_df_coef.csv")
write_csv(edgemodels_vif, "Data/Analysis/df/edgemodels_vif.csv")



```



### Regional Diversity (ERS)
Run best model from above steps interacted with Economic Research Service (ERS) Farm Resource Regions to examine regional change 

The ERS zones are:  

1. Heartland
2. Northern Crescent 
3. Northern Great Plains
4. Prairie Gateway
5. Eastern Uplands 
6. Southern Seaboard
7. Fruitful Rim
8. Basin and Range 
9. Mississippi Portal

```{r}

#Examine regional effects with ERS
data_regional<-fulldata %>% 
  select(FIPS, Year, ASDCode, ERSCode,
         insect_planted, pland_crops, natural_crops_ed, mna_crops, largefarm_planted,
         soysmallgrain_planted, corn_planted, fruitveg_planted,
         msidi, SDI) %>% 
    mutate(ERSCode=factor(ERSCode)) %>% 
    filter(!Year==2002)%>% #Only 3 years of data
  na.omit() %>% #8939 observations (match crops_3yrs and diversity)
  mutate_at(scale, .vars=vars(-FIPS, -Year, -ERSCode, -ASDCode, -insect_planted)) %>%  #Scale by subtracting column mean and dividing by column SD
    rename(Insecticide=insect_planted,
         PercentCrop=pland_crops,
         NaturalCropEdge=natural_crops_ed,
         MeanCropArea=mna_crops,
         LargeFarms=largefarm_planted,
         SoyGrains=soysmallgrain_planted,
         Corn=corn_planted,
         FruitVeg=fruitveg_planted,
         LandDiversity=msidi,
         CropDiversity=SDI)
save(data_regional, file="Data/Analysis/models/df/data_regional.Rda")

lm_regional<-lm(Insecticide~PercentCrop*ERSCode+NaturalCropEdge*ERSCode+MeanCropArea*ERSCode+LargeFarms*ERSCode+
                  SoyGrains*ERSCode+Corn*ERSCode+FruitVeg*ERSCode+LandDiversity*ERSCode+CropDiversity*ERSCode+
                  factor(Year)+factor(ASDCode), data=data_regional)
save(lm_regional, file="Data/Analysis/models/lm_regional.Rda")
df_regional<-broom::tidy(lm_regional) %>% 
  mutate(model="regional") %>% 
  dplyr::filter(!stringr::str_detect(term, "(Intercept)"),
                !stringr::str_detect(term, "factor")) %>% 
    dplyr::filter(!term=="ERSCode2"&!term=="ERSCode3"&!term=="ERSCode4"&
                  !term=="ERSCode5"&!term=="ERSCode6"&!term=="ERSCode7"&
                  !term=="ERSCode8"&!term=="ERSCode9") %>%
  separate(term, c("ERS", "term"), ":") %>% 
  mutate(term = gsub("ERSCode", "", term),
         ERS = gsub("ERSCode", "", ERS),
         term = replace_na(term, 1),
         reference=term) %>% 
  transform(term = ifelse(ERS == 'PercentCrop', ERS, reference),
            ERS = ifelse(ERS == 'PercentCrop', reference, ERS)) %>% 
  transform(term=ifelse(term=="1", ERS, term),
            ERS=ifelse(reference=="1", reference, ERS)) %>% 
  select(-reference) %>% 
  select(term, everything()) %>% 
  arrange(model, term,ERS)
df_coef_regional<-lm_regional %>% 
  clubSandwich::coef_test(vcov = "CR2", cluster = data_regional$ASDCode, test = "Satterthwaite") %>% 
  tibble::rownames_to_column(var = "term") %>% 
  rename(estimate=beta, std.error=SE, statistic=tstat, p.value=p_Satt) %>% 
  dplyr::mutate(model="regional") %>% 
  dplyr::filter(!stringr::str_detect(term, "(Intercept)"),
                !stringr::str_detect(term, "factor")) %>% 
    dplyr::filter(!term=="ERSCode2"&!term=="ERSCode3"&!term=="ERSCode4"&
                  !term=="ERSCode5"&!term=="ERSCode6"&!term=="ERSCode7"&
                  !term=="ERSCode8"&!term=="ERSCode9") %>% 
  separate(term, c("ERS", "term"), ":") %>% 
  mutate(term = gsub("ERSCode", "", term),
         ERS = gsub("ERSCode", "", ERS),
         term = replace_na(term, 1),
         reference=term) %>% 
  transform(term = ifelse(ERS == 'PercentCrop', ERS, reference),
            ERS = ifelse(ERS == 'PercentCrop', reference, ERS)) %>% 
  transform(term=ifelse(term=="1", ERS, term),
            ERS=ifelse(reference=="1", reference, ERS)) %>% 
  select(-reference) %>% 
  select(term, everything()) %>% 
  arrange(model, term,ERS)
# vif_regional<-rownames_to_column(as.data.frame(car::vif(lm_regional)), "term") #(doesn't work because aliased coefficients in the model)


#Write csv for each of the created dataframes
write_csv(df_regional, "Data/Analysis/df/df_regional.csv")
write_csv(df_coef_regional, "Data/Analysis/df/df_coef_regional.csv") 


```

