---
title: "Analysis"
author: "Sofie McComb"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This R Markdown document will perform the panel linear model regressions for determining the relationship of agricultural and landscape variables on insectide use. The regressions are performed in separate R scripts that are sourced below and than analyzed.


Current primary variables to be examined include:  

1. pland_crops
    * Percentage of county with cropland area, in percent 
2. cropintensity 
    * Harvested cropland acres per area of county cropland, in acres/acres
3. SDI
    * Crop diversity, 0-1 value
4. msidi
    * Simpson's landscape diversity, 0-1 value 
5. natural_crops_ed 
    * Shared edge length between natural land and cropland divided by the total county area, in meters/hectares [edge density]  
6. mna_crops
    * Mean patch size in hectares of cropland, in hectares
7. largefarm_planted
    * Acreage of harvested acres for farms >500acres in terms of planted cropland, in acres/acres 

Secondary variables to be examined include:  

1. crop covariates
    * soysmallgrain_planted + corn_planted + fruitveg_planted, all in acres 
 
Analyses are run for all counties pooled together (cp) and by Economic Research Service (ERS) Farm Resource Regions. County and Year fixed effects (and a combination of them) will be run for each regression.
Furthermore, two years (1997 and 2002) and missing data for SDI, so versions will be run excluding these purposefully.
Several combinations of variables and regressions will also be performed. 

## Data Preparation

This section will load the necessary packages and data, and run analyses on the data to examine the natural variation.

### Load Packages

```{r packages, message=F, warning=F}

#Load the needed packages (install first if necessary)
library(tidyverse) #Datatable manipulation
library(purrr) #For reduce function using full_join
library(plm) #Linear models for panel data
library(stats) #For as.formula function
library(car) # For calculating variance inflation factors (vif)
library(rlang) #For xtsum function creation
library(gdata) #For combine in xtsum function
library(broom) #Convert statistical analysis into df
library(reshape2)#For wide to long data format
library(clubSandwich) #for coeftest (cluster robust standard errors)

#Set options
options(scipen=999) #no scientific notation (all)

```


### Load Data

Loading the fulldata dataset created in the DataProcessing.Rmd, which was developed to perform the regression analyses.

```{r data, message=F, warning=F}

load("Data/DataProcessing/df/fulldata.rda")

```

### Examine Data with XTSUM

XTSUM (based on the stata function) examines the overall, within, and between variation found in a dataset.

```{r xtsum, message=F, warning=F}

#Source xtsumR script to examine variation within variables (fips, year) from fulldata and load saved analysis dataframe
source("R/Analysis/xtsumR.R")
#Script both creates R version of xtsum function and perform analyses, put into a dataframe and loaded here.
load("Data/Analysis/xtsum/xtsum_df.Rda")

```


### Prepare Data for Regression

```{r}

#Create dataframe with just the needed regression variables that are stndardized for comparisons    
  finaldata<-fulldata %>% 
  select(FIPS, Year, ERSCode, ASDCode, insect_planted, pland_crops, cropintensity, SDI,
         largefarm_planted, mna_crops, natural_crops_ed, msidi,
         soysmallgrain_planted, corn_planted, fruitveg_planted) %>% 
  mutate_at(scale, .vars=vars(-FIPS, -Year, -ERSCode, -ASDCode, -insect_planted)) #Scale by subtracting column mean and dividing by column SD

#Remove rows with NA value for ASDcode
  finaldata<-finaldata[!is.na(fulldata$ASDCode),]

#Write finaldata to df folder (best place to store even though in Analysis script) to pulled for later regressions
    write_csv(finaldata, "Data/DataProcessing/df/finaldata.csv")
    save(finaldata, file = "Data/DataProcessing/df/finaldata.rda")

```


## Run Panel Linear Model Regressions
Perform the regressions within separate R scripts, perform analyses on the model results, and create dataframes of results across models. The script is sourced directly in the analysis scripts that are used below.


Current versions of regressions to be performed for both pooled counties and by ERS regions include:  

1. Using all 7 primary variables
2. Using 6 primary variables, excluding SDI 
3. Using 6 primary variables, excluding SDI, but just for 2002-2017
4. All secondary crop covariates included, for the three options above

 
Twoways (individual and time) fixed effects models will be run for each regression. Individual will be represented by ASDCode and time will be represetned by year.

Metadata available as Data/Analysis/df/DF_Metadata.txt. File generally describes the columns available in each of the created csv outputs under Data/Analysis/df subfolders. 

Using broom package to put plm model informatino into tidy dataframe format. 
For more information: https://cran.r-project.org/web/packages/broom/vignettes/broom.html

Using clubsandwih package to perform cluster-robust standard errors in tidy format.
For more information: https://cran.r-project.org/web/packages/clubSandwich/vignettes/panel-data-CRVE.html

Using car::vif to run variance  variance inflation factor (vif) to look at multicollinearity between variables 
(VIF of 1=no correlation among predictors, >4 investigate, >10 serious correction)


### 1) Counties Pooled (cp)

The cpmodels script performs the lm models for all counties pooled together and cleans up results into tidy dataframes. Run on standardized variables. Fixed effects include time as years and individual as ASD districts.


```{r cpmodels, message=F, warning=F}

#Script runs the counties pooled (cp) regression models scripts that creates dataframe outputs (models not saved)
source("R/Analysis/cpmodels.R") 

```



### 2) By ERS Region

The ERS zones are:  

1. Heartland
2. Northern Crescent 
3. Northern Great Plains
4. Prairie Gateway
5. Eastern Uplands 
6. Southern Seaboard
7. Fruitful Rim
8. Basin and Range 
9. Mississippi Portal

 
The ERSmodels script performs the lm models for counties interacted with ERS regions and cleans up results into tidy dataframes. Run on standardized variables. Fixed effects include time as years and individual as ASD districts.

```{r ERSmodels, message=FALSE, warning=FALSE, include=FALSE}

#Script runs the ERS (cp) regression models interacted by ERS that creates tidy dataframes (models not saved)
source("R/Analysis/ERSmodels.R")


```



