---
title: "Data Processing"
author: "Sofie McComb"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


This R markdown document will gather and process the data necessary to perform the panel analyses laid out under the Analysis.Rmd. The data sources necessary for the analysis include up-to-date data for the Census of Agriculture (COA), USDA National Agricultural Statistics Service (NASS) Cropland Data Layer (CDL), National Land Cover Database (NLCD), USDA Farm Resource Regions (Economic Service Research: ERS), and USDA Agricultural Statistic Districts (ASD). The necessary data from each dataset will be gathered and combined together to have a full dataset in which each row is a unique county Federal Information Processing Standards (FIPS) code (determined by TIGER 2018 county shapefiles) per year of analysis (1997, 2002, 2007, 2012, 2017) where data availble.

The data to gather includes:  

1. COA
    * County Area, Planted Area, Harvested Area, Failed Area 
    * Total insecticides, Fertilizer, crop categories, irrigation, net cash income, large farm acreage
2. CDL
    * Crop diversity
3. NLCD
    * Patch/diversity metrics: Edge density, edge length, mean patch area, percentage of landscape, landscape diversity
    * Large Crop Patches, calculated from NLCD to represent large farm
4. ERS Regions  
5. ASD Regions  
6. Daily Climate Data

More detail for each dataset will be given below as the data for each dataset is gathered and processed. All final data processed from each source is available under the Data/DataProcessing/df folder as a csv. The dataframe of all combined sources is saved as fulldata, in both csv and rda format (to be loaded into future Analysis.Rmd). Metadata for each individual source final data as well as for fulldata is available in the df folder as separate txt files.


## Data Formatting

```{r packages, message=F, warning=F}

#Load the needed packages, which are loaded in the R scrips as well (install first if necessary)
  library(tidyverse) #Datatable manipulation (all functions)
  library(tools) #For file_path sans_ext (COA.R)
  library(purrr) #For reduce function using full_join (COA.R)
  library(zoo) #For na.locf function (COA.R)
  library(janitor) #Clean colnames (CDL.R)
  library(vegan) #Perform diversity calculation (CDL.R)
  library(readxl) #read excel .xlsx (ERS data)

#Set options
  options(scipen=999) #no scientific notation (all)

```


### 1) Census of Agriculture (CoA)

For 1997-2017:
Census of Agriculture (CoA) datasets were used to define the agricultural properties of each county for use in regression, such as the amount of insectidies used and the area of harvested cropland per county.  

CoA csvs were downloaded individually by agricultural property from the USDA National Agricultural Statistics Service (NASS) Quickstats: https://quickstats.nass.usda.gov/. The downloaded csvs are found in the Data/DataProcessing/CoA folder. An excel sheet of Metadata is provided in the folder, showing snipped images for how each dataset was selected and downloaded on the website. All csvs were labeled as the property being downloaded. Columns are defined by USDA NASS online.

The datasets were combined into one dataframe, and further calculations and clean-up work was performed in order to get the data ready for regressions. 
For 1987 & 1992:
Data given by Ashley Larsen (originally retrieved same location as present CoA except on CD, but not on data viewer online and no longer CDs )

Ensured the downloaded data is the exact same as the current CoA data, and then formatted it in the exact same manner as the present so can have a large CoA dataset from 1987-1992.

More information as well as the data wrangling and caluclations can be found in the R/DataProcessing/COA.R script and COA_8792.R script.

```{r COA, message=F, warning=F}

#Prepare Census of Agriculture data (COA) needed for the regression analyses
source ("R/DataProcessing/COA.R")
source ("R/DataProcessing/COA_8792.R")
#Output saved as Data/DataProcessing/df/coa.csv and Data/DataProcessing/df/coa_8792.csv

#Also combine and save version of COA 1997-2017 and 1987-1992
  #Read in 
  coa_9717<-readr::read_csv("Data/DataProcessing/df/coa.csv") %>% 
    dplyr::select(-income, -fertilizer, -irrigate, -totalplanted_hectares, 
           -income_inflated, -irrigate_planted, -income_planted) #remove columns that are different
  coa_8792<-readr::read_csv("Data/DataProcessing/df/coa_8792.csv")
  
  #Combine dfs
  coa_allyears<-rbind(coa_8792, coa_9717) %>%
    arrange(FIPS, Year)
  
  #Write final all years CoA csv
   write_csv(coa_allyears, "Data/DataProcessing/df/coa_allyears.csv")

```


### 2) Cropland Data Layer (CDL)

Cropland Data Layer (CDL) datasets were used to define crop diversity per county, on the basis of summed crop types and acreage per county.

CDL datasets were downloaded as a zip folder of csvs from the USDA National Agricultural Statistics Service (NASS): https://www.nass.usda.gov/Research_and_Science/Cropland/sarsfaqs2.php. The folder contained csvs of the annual number of pixels or acreages for each crop type per county for 2007-2018. The csvs can be found under Data/DataProcessing/CDL/County_Pixel_Count, and metadata readme txt files from the CDL are also provided in the folder.

The columns of the csvs are category numbers, which were crosswalked to the crop name using the CDL_crosswalk.csv found under Data/DataProcessing/CDL, which was created from data retrieved from:https://www.nass.usda.gov/Research_and_Science/Cropland/docs/CDL_2013_crosswalk.php. 


The total cropland area per county by crop type was summed for the years of interest (2008, 2012, and 2017 to best match other datasets) and then Simpson's diversity index was performed to get a measure of crop diversity per county. Crop acreage accounts for double cropping and crop rotation situations (i.e. counts acreage again if it was used for another crop).

More information as well as the caluclations for crop diversity can be found in the R/DataProcessing/CDL.R script.


```{r CDL, message=F, warning=F}

#Prepare Cropland Data Layer data (CDL) needed for the regression analyses (calculate crop diversity per county)
source ("R/DataProcessing/CDL.R")
#Output saved as Data/DataProcessing/df/cdl.csv

```



### 3) National Land Cover Databse (NLCD)

National Land Cover Database (NLCD) raster files and TIGER 2018 county shapefiles were used to calculate landscape metric analyses at the county level, to be used as metrics of landscape composition and configuration in the regressions. 

NLCD data downlaod from the Multi-Resolution Land Characteristic Consortium (MRLC) as zip folder of multi-year NLCD .img files and supporting information,  from: https://www.mrlc.gov/data. NLCD layers were available for the years 2001, 2004, 2006, 2008, 2011, 2013, and 2016. For the analysis, the years 2001, 2006, 2011, and 2016 were selected in order to best match up with the ag census years of 2002, 2007, 2012, and 2017. 

County borders were defined by the Topologically Integrated Geographic Encoding and Referencing (TIGER) 2018 county shapefile created from U.S. Census Bureau data and avaiable on Data.gov, download at https://catalog.data.gov/dataset/tiger-line-shapefile-2018-nation-u-s-current-county-and-equivalent-national-shapefile.

These datasets are not stored in the repository, as they are too large and take up too much storage. The results from the fragstats analyses are stored in csv format that are available for the years of interest (2001, 2006, 2011, 2016) under the Data/DataProcessing/NF folder. 

The NF.R script under R/DataProcessing provides detailed information for how landscape metric analyses were performed by county using the landscapemetrics package, which replicates FRAGSTATS software functionality in R. More information on fragstats can be found at https://www.umass.edu/landeco/research/fragstats/documents/fragstats.help.4.2.pdf. The script provides the function created to perform theses analyses, but the function must be run from a desktop/cluster where the large NLCD and TIGER spatial files are stored. The script goes into more detail on the time and computer requirements of the computations. 

Calculations performed includeclass metrics of edge density, edge length, percentage landscape, and mean patch area, and the landscape diversity metric. All 5 metrics were performed for all categories, and edge class and landscape metrics were performed for 5 binary reclassifications: forest vs crops, grassland/shrublands vs crops, deciduous forest vs low intensity development (LID), mixed forest vs LID, and natural lands vs crops. The results can be found by year in the Data/DataProcessing/NF folder. A NF_ metadata txt file is availabe in the folder detailing what the column names stand for (same across years).

The NLCD.R script under R/DataProcessing combines all the year csvs found in the NF data folder and then performs additinal caculations and data wrangling needed for regressions. The NLCD script is called on below, as the NF script is already run and the data stored. 


```{r NLCD, message=F, warning=F}

#Prepare National Land Cover Database (NLCD) analyses needed for the regression analyses, which have already been run through fragstats using the R/NF.R script 
source ("R/DataProcessing/NLCD.R")
#Output saved as Data/DataProcessing/df/nlcd.csv

```

Read in Large Crop Patches csv:

```{r}

LCP<-read_csv("Data/DataProcessing/df/LargeCropPatch.csv")

```


### 4) ERS

USDA Farm Resource Regions (Economic Service Research: ERS) data was collected, on the basis of ERS literature https://www.ers.usda.gov/publications/pub-details/?pubid=42299.

An excel sheet crosswalking the FIPS (Federal Information Processing Standards) county codes with the 9 resource regions is available under Data/DataProcessing/ERS. The data was read in and will be combined with all other data regions in order to perform regression analyses on the basis of ERS resource regions.

There is no separate script for this data section.


```{r ERS, message=F, warning=F}

#Read in ERS file, to be combined with other data as is
ERS<-readxl::read_xls("Data/DataProcessing/ERS/ERSRegions_To_Counties.xls")
ERS<-ERS[,1:3]
colnames(ERS)<-c("FIPS", "ERSCode", "ERSName")


```

### 5) ASD

The Agricultural Statistics Districts (ASD) are defined as "a contiguous group of counties having relatively similar agricultural characteristics". More information and the ESRI shapefile can be found at https://data.nal.usda.gov/dataset/nass-quick-stats/resource/5f1173c1-bcb4-4f88-aec0-3bbfee75657f. "The ASD's used by NASS usually divide each state into as many as nine Agricultural Statistics Districts to make data comparison easier. Each district is more homogeneous with respect to agriculture than the state as a whole."

The crosswalk excel sheet loaded in below was provided by Ashley Larsen and was retrieved from the NASS website.

```{r ASD, message=F, warning=F}

#Read in ASD file, to be combined with the other data as is
ASD<-readr::read_csv("Data/DataProcessing/ASD/ASD_County_Crosswalk.csv") %>% 
  select(statecountyfips, StateASD)
colnames(ASD)<-c("FIPS", "ASDCode")

```


### 6) Climate

Daily climate data from Olivier.


Variables to examine: Mean Monthly Temperature (January, April, July, October), Precipitation (Annual, Growing Season),
  Frost Days (annual days with tmin<=32 F), GDD (annual DD based on 50 and 90 F); convert precipitation from in to mm


```{r}

source ("R/DataProcessing/Climate.R")
#Output saved as Data/DataProcessing/df/climate.csv

```


Future climate data from Chelsa- calculated using climate_CHELSEA.R script on R server; need to include here eventually and rename to climate_chelsa


#########################################
## Data Combination

Combine the COA, CDL, NLCD, and ERS data to create final dataframe (fulldata) to be saved and used in regression analyses (Analysis.Rmd). Data and metadata for the fulldata dataframe can be found in the Data/DataProcessing/df folder.

Re-reading in LCP, ERS, and ASD from above if starting from here, instead of running entire Rmd.


```{r combine, message=F, warning=F}

#Read in the datasets
coa<-readr::read_csv("Data/DataProcessing/df/coa.csv")
cdl<-readr::read_csv("Data/DataProcessing/df/cdl.csv")
nlcd<-readr::read_csv("Data/DataProcessing/df/nlcd.csv")
LCP<-read_csv("Data/DataProcessing/df/LargeCropPatch.csv") %>% 
  mutate(FIPS=as.numeric(FIPS))
ERS<-readxl::read_xls("Data/DataProcessing/ERS/ERSRegions_To_Counties.xls") %>% 
  dplyr::select(1:3)
  colnames(ERS)<-c("FIPS", "ERSCode", "ERSName")
ASD<-readr::read_csv("Data/DataProcessing/ASD/ASD_County_Crosswalk.csv") %>% 
  dplyr::select(statecountyfips, StateASD)
  colnames(ASD)<-c("FIPS", "ASDCode")
climate<-readr::read_csv("Data/DataProcessing/df/climate.csv") %>% 
  dplyr::rename(FIPS=fips, Year=year)

#List and merge first four datasets by the unique combination of FIPS and Year Values
fulldata<-list(coa, cdl, nlcd, LCP, climate) %>% 
  reduce(full_join, by=c("FIPS", "Year"))

#Merge with ERS and ASD by just FIPS
fulldata<-list(fulldata, ERS, ASD) %>% 
  reduce(full_join, by=c("FIPS"))


#Drop counties with changed official county borders, etc. issues (same as Larsen 2015 paper)
fulldata<-fulldata %>%
  filter(!(FIPS>=51200 & FIPS<=52000)) %>% #VA counties
  filter(!(FIPS>=2000 & FIPS<3000)) %>% #AK
  filter(!(FIPS>=15000 & FIPS<16000)) %>% #HI
  filter(!(FIPS==08001)&!(FIPS==08013)&!(FIPS==08059)&!(FIPS==08014)&!(FIPS==08123)&
           !(FIPS==30113)&!(FIPS==30031)&!(FIPS==30067)&!(FIPS==08031)&
           !(FIPS==24031)&!(FIPS==24033)&!(FIPS==37031)&!(FIPS==37049)&
           !(FIPS==12045)&!(FIPS==12037)&!(FIPS==11001)&!(FIPS==24510)&
           !(FIPS==29510)&!(FIPS==24510)&!(FIPS==12025)&!(FIPS==12086)) #Counties with changing borders


#Add in columns for natural-crops edge density
  #Have shared edge length between natural land and crops divided by county area (ag)
fulldata<-fulldata %>% #Changed edge metrics to use CountyArea instead (similar output but slighlty more accurate)
    dplyr::mutate(natural_crops_ed=tel_naturalcrops_nc/CountyArea_ha) %>% #meters shared edge per hectare county area
    dplyr::mutate(forest_crops_ed=tel_forestcrop_fc/CountyArea_ha) %>% 
    dplyr::mutate(shrubgrass_crops_ed=tel_shrubgrasscrop_sgc/CountyArea_ha)

#Remove rows with NA value for year
  fulldata<-fulldata[!is.na(fulldata$Year),]
    
#Write fulldata to df folder as all data pulled together (after changes still same row length)
    write_csv(fulldata, "Data/DataProcessing/df/fulldata.csv")
    save(fulldata, file = "Data/DataProcessing/df/fulldata.rda")
    
```


###Forecast NLCD Data for Present (2001-2016) 
Prepared future nlcd data with fragstats calculations on the online R server for faster processing and memory storage. The R scripts used can be found under the server, and the R scripts can be found stored under the R/Future folder as NF_Future and NLCD_Future. NF_Future is the function created to do all the computation, and NLCD_Future carries our the function for the different desired years and gets the NLCD in an appropriate spreadsheet format. Will just put in the saved csvs below, where they were transfered from the online server.

***Possibly need to change present climate data here with forecasted current climate data (just for model testing)

```{r}

#Quick data combination for nlcd

#Read in the NLCD files and rbind (works for now-only files are 2001, 2006, 2011, 2016)
  file_names <- dir("Data/DataProcessing/Future/nlcd_forecast", pattern = ".csv", full.names = TRUE) #files located per year
  nlcd <- do.call(rbind,lapply(file_names,readr::read_csv))

#Change years to match those in the other datasets so can combine by FIPS and years
  #2001 to 2002, 2006 to 2007, 2011 to 2012, and 2016 to 2017
  nlcd$Year[nlcd$Year==2001] <- 2002
  nlcd$Year[nlcd$Year==2006] <- 2007
  nlcd$Year[nlcd$Year==2011] <- 2012
  nlcd$Year[nlcd$Year==2016] <- 2017

#Write final nlcd data to be used in combination with other dataframes
   write_csv(nlcd, "Data/DataProcessing/Future/df/nlcd_forecast.csv")

#############################
  
#Read in forecast nlcd
nlcd<-read_csv("Data/DataProcessing/Future/df/nlcd_forecast.csv") %>% 
  mutate(FIPS=as.numeric(FIPS))

#Read in forecast LCP
LCP<-read_csv("Data/DataProcessing/Future/df/LargeCropPatch_forecast.csv") %>% 
  mutate(FIPS=as.numeric(FIPS))


#Read in the other datasets
coa<-readr::read_csv("Data/DataProcessing/df/coa.csv")
cdl<-readr::read_csv("Data/DataProcessing/df/cdl.csv")

ERS<-readxl::read_xls("Data/DataProcessing/ERS/ERSRegions_To_Counties.xls") %>% 
  dplyr::select(1:3)
  colnames(ERS)<-c("FIPS", "ERSCode", "ERSName")
ASD<-readr::read_csv("Data/DataProcessing/ASD/ASD_County_Crosswalk.csv") %>% 
  dplyr::select(statecountyfips, StateASD)
  colnames(ASD)<-c("FIPS", "ASDCode")
climate<-readr::read_csv("Data/DataProcessing/df/climate.csv") %>% 
  dplyr::rename(FIPS=fips, Year=year)

#List and merge first four datasets by the unique combination of FIPS and Year Values
fulldata<-list(coa, cdl, nlcd, LCP, climate) %>% 
  reduce(full_join, by=c("FIPS", "Year"))

#Merge with ERS and ASD by just FIPS
fulldata<-list(fulldata, ERS, ASD) %>% 
  reduce(full_join, by=c("FIPS"))


#Drop counties with changed official county borders, etc. issues (same as Larsen 2015 paper)
fulldata<-fulldata %>%
  filter(!(FIPS>=51200 & FIPS<=52000)) %>% #VA counties
  filter(!(FIPS>=2000 & FIPS<3000)) %>% #AK
  filter(!(FIPS>=15000 & FIPS<16000)) %>% #HI
  filter(!(FIPS==08001)&!(FIPS==08013)&!(FIPS==08059)&!(FIPS==08014)&!(FIPS==08123)&
           !(FIPS==30113)&!(FIPS==30031)&!(FIPS==30067)&!(FIPS==08031)&
           !(FIPS==24031)&!(FIPS==24033)&!(FIPS==37031)&!(FIPS==37049)&
           !(FIPS==12045)&!(FIPS==12037)&!(FIPS==11001)&!(FIPS==24510)&
           !(FIPS==29510)&!(FIPS==24510)&!(FIPS==12025)&!(FIPS==12086)) #Counties with changing borders


#Add in columns for natural-crops edge density
  #Have shared edge length between natural land and crops divided by county area (ag)
fulldata<-fulldata %>% #Changed edge metrics to use CountyArea instead (similar output but slighlty more accurate)
    dplyr::mutate(natural_crops_ed=tel_naturalcrops_nc/CountyArea_ha) %>% #meters shared edge per hectare county area
    dplyr::mutate(forest_crops_ed=tel_forestcrop_fc/CountyArea_ha) %>% 
    dplyr::mutate(shrubgrass_crops_ed=tel_shrubgrasscrop_sgc/CountyArea_ha)

  
#Remove rows with NA value for year
  fulldata<-fulldata[!is.na(fulldata$Year),]

  #Name as fulldata_forecast
  fulldata_forecast<-fulldata
    
#Write fulldata_forecast to df folder as all data pulled together
    write_csv(fulldata_forecast, "Data/DataProcessing/Future/df/fulldata_forecast.csv")
    save(fulldata_forecast, file = "Data/DataProcessing/Future/df/fulldata_forecast.rda")
    

```


#Foreast Data: All 4 current years, 2 scenarios (NLCD B1,A2)-using forecasted current chelsa data

Prepared future nlcd data with fragstats calculations on the online R server for faster processing and memory storage. The R scripts used can be found under the server, and the R scripts can be found stored under the R/Future folder as Final_NLCD_Future. 


```{r}


#############################
  
#Read in forecast nlcd (include LCP)
nlcd<-read_csv("Data/DataProcessing/Future/df/nlcd_forecast_current.csv") %>% 
  mutate(FIPS=as.numeric(FIPS))
   
   #Change years to match those in the other datasets so can combine by FIPS and years
  #2001 to 2002, 2006 to 2007, 2011 to 2012, and 2016 to 2017
  nlcd$Year[nlcd$Year==2001] <- 2002
  nlcd$Year[nlcd$Year==2006] <- 2007
  nlcd$Year[nlcd$Year==2011] <- 2012
  nlcd$Year[nlcd$Year==2016] <- 2017


#Read in the other datasets
coa<-readr::read_csv("Data/DataProcessing/df/coa.csv")
cdl<-readr::read_csv("Data/DataProcessing/df/cdl.csv")

ERS<-readxl::read_xls("Data/DataProcessing/ERS/ERSRegions_To_Counties.xls") %>% 
  dplyr::select(1:3)
  colnames(ERS)<-c("FIPS", "ERSCode", "ERSName")
ASD<-readr::read_csv("Data/DataProcessing/ASD/ASD_County_Crosswalk.csv") %>% 
  dplyr::select(statecountyfips, StateASD)
  colnames(ASD)<-c("FIPS", "ASDCode")
climate<-readr::read_csv("Data/DataProcessing/Climate/forecastedclimate.csv") %>% 
  filter(Scenario=="Current") %>% 
  dplyr::mutate(FIPS=as.numeric(FIPS)) %>% 
  dplyr::select(-Scenario)
  
#List and merge datasets by the unique combination of FIPS and Year Values
fulldata<-list(coa, cdl, nlcd) %>% 
  reduce(full_join, by=c("FIPS", "Year"))

#Merge with ERS and ASD by just FIPS
fulldata<-list(fulldata, ERS, ASD) %>% 
  reduce(full_join, by=c("FIPS"))

#Merge climate with fulldata-ensure climate repeats for all years and scenarios of fulldata
fulldata<-list(fulldata, climate) %>% 
  reduce(full_join, by="FIPS")
#52603 rows


#Drop counties with changed official county borders, etc. issues (same as Larsen 2015 paper)
fulldata<-fulldata %>%
  filter(!(FIPS>=51200 & FIPS<=52000)) %>% #VA counties
  filter(!(FIPS>=2000 & FIPS<3000)) %>% #AK
  filter(!(FIPS>=15000 & FIPS<16000)) %>% #HI
  filter(!(FIPS==08001)&!(FIPS==08013)&!(FIPS==08059)&!(FIPS==08014)&!(FIPS==08123)&
           !(FIPS==30113)&!(FIPS==30031)&!(FIPS==30067)&!(FIPS==08031)&
           !(FIPS==24031)&!(FIPS==24033)&!(FIPS==37031)&!(FIPS==37049)&
           !(FIPS==12045)&!(FIPS==12037)&!(FIPS==11001)&!(FIPS==24510)&
           !(FIPS==29510)&!(FIPS==24510)&!(FIPS==12025)&!(FIPS==12086)) #Counties with changing borders


#Add in columns for natural-crops edge density
  #Have shared edge length between natural land and crops divided by county area (ag)
fulldata<-fulldata %>% #Changed edge metrics to use CountyArea instead (similar output but slighlty more accurate)
    dplyr::mutate(natural_crops_ed=tel_naturalcrops_nc/CountyArea_ha) %>% #meters shared edge per hectare county area
    dplyr::mutate(forest_crops_ed=tel_forestcrop_fc/CountyArea_ha) %>% 
    dplyr::mutate(shrubgrass_crops_ed=tel_shrubgrasscrop_sgc/CountyArea_ha)

  
#Remove rows with NA value for year
  fulldata<-fulldata[!is.na(fulldata$Year),]

  #Name as fulldata_forecast
  fulldata_forecast_allscenarios<-fulldata %>% 
    dplyr::select(FIPS, Year, Scenario, everything()) %>% #Put these rows before all others
    filter(Scenario=="B1"|Scenario=="A2") #A1B and B2 are not close enough to RCP; B1=4.5 and A2=8.5
    
#Write fulldata_forecast to df folder as all data pulled together
    write_csv(fulldata_forecast_allscenarios, "Data/DataProcessing/Future/df/fulldata_forecast_allscenarios.csv")
    save(fulldata_forecast_allscenarios, file = "Data/DataProcessing/Future/df/fulldata_forecast_allscenarios.rda")
    

```




### Forecast Data: 2050, all scenarios (B1, A2); chelsea climate

```{r}

 #Read in nlcd_2050 (contains LCP and all needed calculations)
nlcd_2050<-read_csv("Data/DataProcessing/Future/df/nlcd_2050.csv") %>% 
  mutate(FIPS=as.numeric(FIPS))

#Read in the other datasets (ERS and ASD)
ERS<-readxl::read_xls("Data/DataProcessing/ERS/ERSRegions_To_Counties.xls") %>% 
  dplyr::select(1:3)
  colnames(ERS)<-c("FIPS", "ERSCode", "ERSName")
ASD<-readr::read_csv("Data/DataProcessing/ASD/ASD_County_Crosswalk.csv") %>% 
  dplyr::select(statecountyfips, StateASD)
  colnames(ASD)<-c("FIPS", "ASDCode")

#Merge nlcd with ERS and ASD by just FIPS
fulldata<-list(nlcd_2050, ERS, ASD) %>% 
  reduce(full_join, by=c("FIPS")) %>% 
   filter(Scenario=="B1"|Scenario=="A2") #only keep B1 and A2

climate<-readr::read_csv("Data/DataProcessing/Climate/forecastedclimate.csv") %>% 
  filter(Scenario!="Current") %>% 
  dplyr::mutate(FIPS=as.numeric(FIPS))

climate$Scenario<-ifelse(climate$Scenario=="RCP45", "B1", ifelse(climate$Scenario=="RCP85", "A2", climate$Scenario))
  #Switch SRES to RCP

#Merge fulldata with climate
fulldata<-list(fulldata, climate) %>% 
  reduce(full_join, by=c("FIPS", "Scenario"))

#Drop counties with changed official county borders, etc. issues (same as Larsen 2015 paper)
fulldata<-fulldata %>%
  filter(!(FIPS>=51200 & FIPS<=52000)) %>% #VA counties
  filter(!(FIPS>=2000 & FIPS<3000)) %>% #AK
  filter(!(FIPS>=15000 & FIPS<16000)) %>% #HI
  filter(!(FIPS==08001)&!(FIPS==08013)&!(FIPS==08059)&!(FIPS==08014)&!(FIPS==08123)&
           !(FIPS==30113)&!(FIPS==30031)&!(FIPS==30067)&!(FIPS==08031)&
           !(FIPS==24031)&!(FIPS==24033)&!(FIPS==37031)&!(FIPS==37049)&
           !(FIPS==12045)&!(FIPS==12037)&!(FIPS==11001)&!(FIPS==24510)&
           !(FIPS==29510)&!(FIPS==24510)&!(FIPS==12025)&!(FIPS==12086)) #Counties with changing borders

#Remove rows with NA value for year (only ERS/ASD data, no NLCD)
  fulldata<-fulldata[!is.na(fulldata$Year),]

  #Name as fulldata_2050
  fulldata_2050<-fulldata
    
#Write fulldata_2050 to df folder as all data pulled together
    write_csv(fulldata_2050, "Data/DataProcessing/Future/df/fulldata_2050.csv")
    save(fulldata_2050, file = "Data/DataProcessing/Future/df/fulldata_2050.rda")



```


### Fulldata for CoA only all years


```{r combine, message=F, warning=F}

#Read in the datasets
coa_allyears<-readr::read_csv("Data/DataProcessing/df/coa_allyears.csv")
ERS<-readxl::read_xls("Data/DataProcessing/ERS/ERSRegions_To_Counties.xls") %>% 
  select(1:3)
  colnames(ERS)<-c("FIPS", "ERSCode", "ERSName")
ASD<-readr::read_csv("Data/DataProcessing/ASD/ASD_County_Crosswalk.csv") %>% 
  select(statecountyfips, StateASD)
  colnames(ASD)<-c("FIPS", "ASDCode")
climate<-readr::read_csv("Data/DataProcessing/df/climate.csv") %>% 
  dplyr::rename(FIPS=fips, Year=year)

#Merge with CoA with ERS and ASD by just FIPS
fulldata<-list(coa_allyears, climate) %>% 
  reduce(full_join, by=c("FIPS", "Year"))


fulldata<-list(fulldata, ERS, ASD) %>% 
  reduce(full_join, by=c("FIPS"))


#Drop counties with changed official county borders, etc. issues (same as Larsen 2015 paper)
fulldata<-fulldata %>%
  filter(!(FIPS>=51200 & FIPS<=52000)) %>% #VA counties
  filter(!(FIPS>=2000 & FIPS<3000)) %>% #AK
  filter(!(FIPS>=15000 & FIPS<16000)) %>% #HI
  filter(!(FIPS==08001)&!(FIPS==08013)&!(FIPS==08059)&!(FIPS==08014)&!(FIPS==08123)&
           !(FIPS==30113)&!(FIPS==30031)&!(FIPS==30067)&!(FIPS==08031)&
           !(FIPS==24031)&!(FIPS==24033)&!(FIPS==37031)&!(FIPS==37049)&
           !(FIPS==12045)&!(FIPS==12037)&!(FIPS==11001)&!(FIPS==24510)&
           !(FIPS==29510)&!(FIPS==24510)&!(FIPS==12025)&!(FIPS==12086)) #Counties with changing borders

#Remove rows with NA value for year
  fulldata<-fulldata[!is.na(fulldata$Year),]
  fulldata_coa_allyrs<-fulldata #save as final name
    
#Write fulldata to df folder as all data pulled together (after changes still same row length)
    write_csv(fulldata_coa_allyrs, "Data/DataProcessing/df/fulldata_coa_allyrs.csv")
    save(fulldata_coa_allyrs, file = "Data/DataProcessing/df/fulldata_coa_allyrs.rda")
    
```







