---
title: "Present_AllVariables"
author: "Sofie McComb"
date: "February 18, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This R Markdown document will perform the panel linear model regressions for determining the relationship of agricultural and landscape variables on insectide use in the present-day.

Twoways (individual and time) fixed effects models will be run for each regression. Individual will be represented by ASDCode and time will be represented by year.

 
## Data Preparation

This section will load the necessary packages and data

#### Load Packages

```{r packages, message=F, warning=F}

#Load the needed packages (install first if necessary)
library(tidyverse) #Datatable manipulation
library(purrr) #For reduce function using full_join
library(car) # For calculating variance inflation factors (vif)
library(broom) #Convert statistical analysis into df
library(reshape2)#For wide to long data format
library(clubSandwich) #for coeftest (cluster robust standard errors)

#Set options
options(scipen=999) #no scientific notation (all)

```


#### Load Data

Loading the fulldata dataset created in the DataProcessing.Rmd, which was developed to perform the regression analyses,
as well as fulldata_forecast for the forecasted versions of the 4 NLCD

```{r data, message=F, warning=F}

load("Data/DataProcessing/df/fulldata.rda")
load("Data/DataProcessing/Future/df/fulldata_forecast.rda")

```




## Panel Regression Analyses

###Model
Just trying everything with fulldate (try with fulldata forecast afterwards)

```{r}

data_model_na<-fulldata %>% 
  dplyr::select(FIPS, Year, ASDCode, ERSCode,
           insect_planted, pland_crops, Prop_LCP, 
           soysmallgrain_planted, corn_planted, fruitveg_planted,
           natural_crops_ed, msidi, 
           annual_prcp, growingseason_temp, growingseason_prcp,
           Jan_tmean_avg, Apr_tmean_avg, Jul_tmean_avg, Oct_tmean_avg,
           annual_GDD, tmin_avg_JanFebMar, tmax_avg_JunJulAug,
           bio5, bio6) %>% 
  na.omit() %>% 
  dplyr::select(FIPS, Year, ASDCode, ERSCode,
           insect_planted, 
           # pland_crops, Prop_LCP, 
           # soysmallgrain_planted, corn_planted, fruitveg_planted,
           # natural_crops_ed, msidi 
           # annual_prcp, 
           # growingseason_temp, 
           growingseason_prcp,
           # Jan_tmean_avg, Apr_tmean_avg, Jul_tmean_avg, Oct_tmean_avg,
           annual_GDD, 
           tmin_avg_JanFebMar, tmax_avg_JunJulAug
           # bio5, bio6
           ) #11333
dat_fips<- data_model_na%>%
    group_by(FIPS) %>%
    summarise(count=n()) %>% 
  filter(count==4) %>% 
  dplyr::select(FIPS) #2612 fips
data_model<-left_join(dat_fips, data_model_na)%>%
  # mutate_at(scale, .vars=vars(-FIPS, -Year, -ERSCode, -ASDCode, -insect_planted)) %>%  #Scale by subtracting column mean and dividing by column SD
    rename(Insecticide=insect_planted,
               # PercentCrop=pland_crops,
               # LargeCropPatches=Prop_LCP,
               # SoyGrains=soysmallgrain_planted,
               # Corn=corn_planted,
               # FruitVeg=fruitveg_planted,
               # NaturalCropEdge=natural_crops_ed,
               # LandDiversity=msidi
               # AnnualPrecipitation=annual_prcp,
           GrowingSeasonPrecipitation=growingseason_prcp,
           # GrowingSeasonTemperature=growingseason_temp,
               AnnualGDD=annual_GDD,
               # JanuaryTmean=Jan_tmean_avg,
               # AprilTmean=Apr_tmean_avg,
               # JulyTmean=Jul_tmean_avg,
               # OctoberTmean=Oct_tmean_avg,
               WinterTminavg=tmin_avg_JanFebMar,
               SummerTmaxavg=tmax_avg_JunJulAug
               # TmaxWarmestMonth=bio5,
               # TminColdestMonth=bio6
           )

    lm_model<-lm(Insecticide~
                 #   PercentCrop+LargeCropPatches+
                 # SoyGrains+Corn+FruitVeg+
                 # NaturalCropEdge+LandDiversity+
                   # AnnualPrecipitation+ 
                   GrowingSeasonPrecipitation+ 
                   # GrowingSeasonTemperature+
                   AnnualGDD+
                   # JanuaryTmean+AprilTmean+JulyTmean+OctoberTmean+
                   WinterTminavg+SummerTmaxavg+
                   # TmaxWarmestMonth+TminColdestMonth+
                factor(Year)+factor(ASDCode), data=data_model)
df_coef_model<-lm_model %>% 
  clubSandwich::coef_test(vcov = "CR2", cluster = data_model$ASDCode, test = "Satterthwaite")


stargazer::stargazer(lm_model,
                     type="text", omit=c("ASDCode","Year"),
                     out="Data/Present/stargazer/Present_AllVariables_test.txt",
                     omit.stat=c("LL","ser","f"),
                     se = list(df_coef_model[,2]),
                     p=list(df_coef_model[,5]))


calc_model_stats<-function(modelname){
  modelnm<-modelname
  statsdf<-as.data.frame(cbind(nobs(modelnm),
                 summary(modelnm)$adj.r.squared,
                 stats::AIC(modelnm),
                 stats::BIC(modelnm)))
  return(statsdf)
}

#Calc stats for each model
stats_model<-calc_model_stats(lm_model)
colnames(stats_model)<-c("Observations", "Adjusted R2", "AIC", "BIC")
stats_model


calc_vif<-function(modelname){
  modelnm<-modelname
  vif_df<-rownames_to_column(as.data.frame(car::vif(modelnm))) %>% 
    dplyr::select(1, 4)
  colnames(vif_df)<-c("Variable", "VIF")
  return(vif_df)
}

vif_model<-calc_vif(lm_model) %>% rename(Model=VIF)
vif_model

```


