---
title: "Present_AllVariables"
author: "Sofie McComb"
date: "February 18, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This R Markdown document will perform the panel linear model regressions for determining the relationship of agricultural and landscape variables on insectide use in the present-day.

Twoways (individual and time) fixed effects models will be run for each regression. Individual will be represented by ASDCode and time will be represented by year.

 
## Data Preparation

This section will load the necessary packages and data

#### Load Packages

```{r packages, message=F, warning=F}

#Load the needed packages (install first if necessary)
library(tidyverse) #Datatable manipulation
library(purrr) #For reduce function using full_join
library(car) # For calculating variance inflation factors (vif)
library(broom) #Convert statistical analysis into df
library(reshape2)#For wide to long data format
library(clubSandwich) #for coeftest (cluster robust standard errors)

#Set options
options(scipen=999) #no scientific notation (all)

```


#### Load Data

Loading the fulldata dataset created in the DataProcessing.Rmd, which was developed to perform the regression analyses,
as well as fulldata_forecast for the forecasted versions of the 4 NLCD

```{r data, message=F, warning=F}

load("Data/DataProcessing/df/fulldata.rda")
load("Data/DataProcessing/Future/df/fulldata_forecast.rda")

```

