---
title: "Supplementary"
author: "Sofie McComb"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Saved files for Supplementary Rmd do not have their own folder under Data, and instead can be found under the visualize folder, so that all present-day visualizations can be kept together for easy viewing.


##Load Packages

```{r}
#Load the needed packages (install first if necessary)
library(tidyverse) #Datatable manipulation (all functions)
library(xtable) #Create VIF tables with xtable
library(corrplot) #Correlation Plot
library(RColorBrewer) #Color Brewer Palettes
library(sf)#shapefiles
library(ggplot2) #Plotting ggplot
library(stargazer)#Making regression tables
library(data.table)#Table format needed for conley
library(lfe)#Need for felm, for conley
library(Rcpp)#Need to read .cpp file for conley
library(RcppArmadillo)#Need to read .cpp file for conley
library(dendextend)#extending dendogram objects, for conley maybe
library(tmap) #Make vector maps 
library(clubSandwich) #For coeftest

#Set options
  options(scipen=999) #no scientific notation (all)

```



## VIF Tables
Make table with VIFs or maybe a correlation plot (library = corrplot) for the landscape and patch metrics (Percent crop, edge density crops, mean patch size crops, large farms, crop diversity, landscape diversity) for final best model. 

```{r}

#Load final models with edge crops and with natural-crop edges
vif_diversity<-readr::read_csv("Data/Analysis/df/vif_diversity.csv")
edgemodels_vif<-readr::read_csv("Data/Analysis/df/edgemodels_vif.csv")

vif_cropedge<-vif_diversity[,c(1,4)] %>% 
  mutate(Variable=c("Percent Cropland", "Crop Edge Density", "Average Crop Area", 
                    "Proportion Large Farms", "Proportion soybeans & small grains", 
                    "Proportion corn", "Proportion fruit & vegetables", 
                    "Landscape Diversity", "Cropland Diversity", "Year", "ASD Code")) %>% 
  select(3,2)
colnames(vif_cropedge)<-c("Variable", "VIF")

vif_naturalcropedge<-edgemodels_vif %>%  
  filter(model=="natural") %>% 
    mutate(Variable=c("Percent Cropland", "Natural-Crop Edge Density", "Average Crop Area", 
                    "Proportion Large Farms", "Proportion soybeans & small grains", 
                    "Proportion corn", "Proportion fruit & vegetables", 
                    "Landscape Diversity", "Cropland Diversity", "Year", "ASD Code")) %>% 
  select(6,4)
colnames(vif_naturalcropedge)<-c("Variable", "VIF")

write_csv(vif_cropedge, "Data/Visualize/VIF/cropedge_vif_table.csv")
write_csv(vif_naturalcropedge, "Data/Visualize/VIF/naturalcropedge_vif_table.csv")

#Print xtables to html, then snip to PNGs
print.xtable(xtable(vif_cropedge), type="html", file="Data/Visualize/VIF/cropedge_vif_table.html",include.rownames=F)
print.xtable(xtable(vif_naturalcropedge), type="html", file="Data/Visualize/VIF/naturalcropedge_vif_table.html",include.rownames=F)

#############
#Correlation Plots for best models-with crop edge and natural-crop edge
# load("Data/Analysis/models/df/data_diversity.Rda")
# load("Data/Analysis/models/df/data_natural.Rda")
# 
# corrdf_cropedge<-data_diversity[,6:14] #Only the covariates
# corrdf_natcropedge<-data_natural[,6:14]#Only the covariates

# #Plot and save correlation matrices
# png(filename="Data/Visualize/VIF/cropedge_corrplot.png",width=600, height=600)
# corrplot::corrplot(cor(corrdf_cropedge), type = "upper", order = "hclust", 
#          tl.col = "black", tl.srt = 45,col=brewer.pal(n=8, name="RdYlBu"))
# dev.off()
# 
# png(filename="Data/Visualize/VIF/natcropedge_corrplot.png", width=600, height=600)
# corrplot::corrplot(cor(corrdf_natcropedge), type = "upper", order = "hclust", 
#          tl.col = "black", tl.srt = 45,col=brewer.pal(n=8, name="RdYlBu"))
# dev.off()

#Use data_natural as base, demean the covariates based on ASDCode and Year
transform(dd, 
    newA = priceA-ave(priceA, weekyear)-ave(priceA, Location_Id),
    newB = priceB-ave(priceB, weekyear)-ave(priceB, Location_Id)
)

load("Data/DataProcessing/df/fulldata.rda")
data_correlation<-fulldata %>% 
  select(FIPS, Year, ASDCode, ERSCode,
         insect_planted, pland_crops, natural_crops_ed, mna_crops, largefarm_planted,
         soysmallgrain_planted, corn_planted, fruitveg_planted,
         msidi, SDI) %>% 
    filter(!Year==2002)%>% #Only 3 years of data
  na.omit() %>% #8939 observations (match crops_3yrs and diversity)
    rename(Insecticide=insect_planted) %>% 
  mutate(PercentCrop=pland_crops-ave(pland_crops, Year)-ave(pland_crops, ASDCode),
         NaturalCropEdge=natural_crops_ed-ave(natural_crops_ed, Year)-ave(natural_crops_ed, ASDCode),
         MeanCropArea=mna_crops-ave(mna_crops, Year)-ave(mna_crops, ASDCode),
         LargeFarms=largefarm_planted-ave(largefarm_planted, Year)-ave(largefarm_planted, ASDCode),
         SoyGrains=soysmallgrain_planted-ave(soysmallgrain_planted, Year)-ave(soysmallgrain_planted, ASDCode),
         Corn=corn_planted-ave(corn_planted, Year)-ave(corn_planted, ASDCode),
         FruitVeg=fruitveg_planted-ave(fruitveg_planted, Year)-ave(fruitveg_planted, ASDCode),
         LandDiversity=msidi-ave(msidi, Year)-ave(msidi, ASDCode),
         CropDiversity=SDI-ave(SDI, Year)-ave(SDI, ASDCode)) %>% 
  select(PercentCrop, NaturalCropEdge, MeanCropArea, LargeFarms, SoyGrains, Corn, FruitVeg, LandDiversity, CropDiversity)

#Using this site as basis:https://stackoverflow.com/questions/27431735/demeaning-data-on-multiple-levels-in-r

png(filename="Data/Visualize/VIF/demeaned_corrplot.png",width=600, height=600)
corrplot::corrplot(cor(data_correlation), type = "upper", order = "hclust", 
          tl.col = "black", tl.srt = 45,col=brewer.pal(n=8, name="RdYlBu"))
dev.off()



```


## Conley Standard Errors
Perform Conley standard errors using best model on centroids of counties (200 km, no time lags) to examine spatial autocorrelation on final best model, without regional effects (http://www.trfetzer.com/using-r-to-estimate-spatial-hac-errors-per-conley/)

### Create linear model

```{r}


# Loading R function to compute Conley SEs:
#Did not work by itself, but files are downloaded
    # source("~/Dropbox/ConleySEs/ConleySEs_17June2015.R")#original
    # install.packages("devtools")
    # library(devtools)
    # install_github("shommazumder/shomR")
    # library(shomR)

#Loading sample data and preparing for model
load("Data/DataProcessing/df/fulldata.rda")
data_conley<-fulldata %>% #Starting same as data_natural
  select(FIPS, Year, ASDCode, ERSCode,
         insect_planted, pland_crops, natural_crops_ed, mna_crops, largefarm_planted,
         soysmallgrain_planted, corn_planted, fruitveg_planted,
         msidi, SDI) %>% 
    filter(!Year==2002)%>% #Only 3 years of data
  na.omit() %>% #8939 observations (match crops_3yrs and diversity)
  mutate_at(scale, .vars=vars(-FIPS, -Year, -ERSCode, -ASDCode, -insect_planted)) %>%  #Scale by subtracting column mean and dividing by column SD
    rename(Insecticide=insect_planted,
         PercentCrop=pland_crops,
         NaturalCropEdge=natural_crops_ed,
         MeanCropArea=mna_crops,
         LargeFarms=largefarm_planted,
         SoyGrains=soysmallgrain_planted,
         Corn=corn_planted,
         FruitVeg=fruitveg_planted,
         LandDiversity=msidi,
         CropDiversity=SDI)

#Need to add lat and lon values from map of FIPS
counties<-read_sf(dsn = "C:/Users/shemc/Documents/UCSB/NLCD/Data/TIGER2018_Counties", layer = "tl_2018_us_county") %>%  
  dplyr::mutate(FIPS=paste0(STATEFP,COUNTYFP))
counties<-st_transform(counties, "+proj=aea +lat_1=29.5 +lat_2=45.5 +lat_0=23 +lon_0=-96 +x_0=0 +y_0=0 +ellps=WGS84
                     +towgs84=0,0,0,-0,-0,-0,0 +units=m +no_defs ") #Project counties to nlcd projection
contig48_counties<-subset(counties,counties$STATEFP!="02"& counties$STATEFP!="15"&
                            counties$STATEFP!="60"&counties$STATEFP!="66"&
                            counties$STATEFP!="69"&counties$STATEFP!="72"&
                            counties$STATEFP!="74"&counties$STATEFP!="78") %>% 
  select(FIPS, geometry)

#Get centroids
sf_cent <- st_centroid(contig48_counties)
sf_coord<-st_coordinates(sf_cent)
fips_coords<-cbind(sf_cent, sf_coord) %>% 
  mutate(FIPS=as.numeric(FIPS))

#Join data with regression data
conleydf<-data_conley %>% 
  left_join(fips_coords) %>% 
  rename(lat=X, lon=Y)

#Double check calculated correctly by plotting (looks good)
  # library(tmap)
  # tm_shape(contig48_counties)+tm_fill(col="white")+
  #   tm_borders(col = "gray40", lwd = 1)+
  # tm_shape(sf_cent) + 
  #   tm_dots()


lm_conley<-felm(Insecticide~PercentCrop+NaturalCropEdge+MeanCropArea+LargeFarms+
                  SoyGrains+Corn+FruitVeg+LandDiversity+CropDiversity -1 |Year +ASDCode | 0 | lat +lon,
                data=conleydf, keepCX=TRUE) #Identical coefficients to lm_natural, slightly different SE

conley_coef<-coefficients(lm_conley) %>%
  round(3) %>% 
  data.frame() %>% 
  tibble::rownames_to_column()
colnames(conley_coef)<-c("Variable", "Estimate")

conley_cse<-lm_conley$cse %>% 
  round(3) %>% 
  data.frame() %>% 
  tibble::rownames_to_column()
colnames(conley_cse)<-c("Variable", "Cluster SE")

stargazer::stargazer(lm_conley, type="text", out="Data/Visualize/conley/conley_stargazer_table.txt",
                               covariate.labels=c("Percent Cropland", "Natural-Crop Edge Density", 
                                                  "Average Crop Area", "Proportion Large Farms",
                             "Proportion soybeans and small grains", "Proportion corn", "Proportion fruit and vegetables",
                             "Landscape Diversity", "Cropland Diversity"),
                     omit.stat=c("LL","ser","f"))


    # Use the felm() from the lfe package to estimate model with year and county fixed effects.
    # Two important points:
    # (1) We specify our latitude and longitude coordinates as the cluster variables, so that they are included in the output (m).
    # (2) We specify keepCx = TRUE, so that the centered data is included in the output (m).

```

### Perform Conley SE

```{r}

#Conley function will not work (not the downloaded one, or me recreating it)
  #So have created the function effectively below, still can call the cpp function and iterate Obs function
  #Code developed from https://github.com/shommazumder/shomR

#0 lag time and 200km

#Define variables
reg = lm_conley
unit = "ASDCode" 
time = "Year"
lat = "lat" 
lon = "lon"
dist_fn = "SH" #default is "haversine"
dist_cutoff = 200 #default is 500
lag_cutoff = 0 #default is 5
cores = 1
verbose = TRUE
kernel = "bartlett" 
# lat_scale = 111 #seem not to need
balanced_pnl = FALSE

pkgs <- c("data.table", "lfe", "geosphere", "Rcpp", "RcppArmadillo")
invisible(sapply(pkgs, require, character.only = TRUE))
library(Rcpp)
sourceCpp("R/Visualize/cpp-functions.cpp")


  Fac2Num <- function(x) {as.numeric(as.character(x))}
  source("R/Visualize/iterateObs.R")
  if(cores > 1) {invisible(library(parallel))}
  
  if(class(reg) == "felm") {
    Xvars <- rownames(reg$coefficients)
    dt = data.table(reg$cY, reg$cX,
                    fe1 = Fac2Num(reg$fe[[1]]),
                    fe2 = Fac2Num(reg$fe[[2]]),
                    coord1 = Fac2Num(reg$clustervar[[1]]),
                    coord2 = Fac2Num(reg$clustervar[[2]]))
    setnames(dt,
             c("fe1", "fe2", "coord1", "coord2"),
             c(names(reg$fe), names(reg$clustervar)))
    dt = dt[, e := as.numeric(reg$residuals)]
    
  } else {
    message("Model class not recognized.")
    break
  }
  
  n <- nrow(dt)
  k <- length(Xvars)
  
  # Renaming variables:
  orig_names <- c(unit, time, lat, lon)
  new_names <- c("unit", "time", "lat", "lon")
  setnames(dt, orig_names, new_names)
  
  # Empty Matrix:
  XeeX <- matrix(nrow = k, ncol = k, 0)
  
  #================================================================
  # Correct for spatial correlation:
  timeUnique <- unique(dt[, time])
  Ntime <- length(timeUnique)
  setkey(dt, time)
  
  if(verbose){message("Starting to loop over time periods...")}
  
  if(balanced_pnl){
    sub_dt <- dt[time == timeUnique[1]]
    lat <- sub_dt[, lat]; lon <- sub_dt[, lon]; rm(sub_dt)
    
    if(balanced_pnl & verbose){message("Computing Distance Matrix...")}
    
    d <- DistMat(cbind(lat, lon), cutoff = dist_cutoff, kernel, dist_fn)
    rm(list = c("lat", "lon"))
  }
  
  if(cores == 1) {
    XeeXhs <- lapply(timeUnique, function(t) iterateObs(sub_index = t,
                                                        type = "spatial", cutoff = dist_cutoff))
  } else {
    XeeXhs <- mclapply(timeUnique, function(t) iterateObs(sub_index = t,
                                                          type = "spatial", cutoff = dist_cutoff), mc.cores = cores)
  }
  
  if(balanced_pnl){rm(d)}
  
  # First Reduce:
  XeeX <- Reduce("+",  XeeXhs)
  
  # Generate VCE for only cross-sectional spatial correlation:
  X <- as.matrix(dt[, eval(Xvars), with = FALSE])
  invXX <- solve(t(X) %*% X) * n
  
  V_spatial <- invXX %*% (XeeX / n) %*% invXX / n
  
  V_spatial <- (V_spatial + t(V_spatial)) / 2
  
  if(verbose) {message("Computed Spatial VCOV.")}
  
  #================================================================
  # Correct for serial correlation:
  panelUnique <- unique(dt[, unit])
  Npanel <- length(panelUnique)
  setkey(dt, unit)
  
  if(verbose){message("Starting to loop over units...")}
  
  if(cores == 1) {
    XeeXhs <- lapply(panelUnique, function(t) iterateObs(sub_index = t,
                                                         type = "serial", cutoff = lag_cutoff))
  } else {
    XeeXhs <- mclapply(panelUnique,function(t) iterateObs(sub_index = t,
                                                          type = "serial", cutoff = lag_cutoff), mc.cores = cores)
  }
  
  XeeX_serial <- Reduce("+",  XeeXhs)
  
  XeeX <- XeeX + XeeX_serial
  
  V_spatial_HAC <- invXX %*% (XeeX / n) %*% invXX / n
  V_spatial_HAC <- (V_spatial_HAC + t(V_spatial_HAC)) / 2
  
  return_list <- list(
    "OLS" = reg$vcv,
    "Spatial" = V_spatial,
    "Spatial_HAC" = V_spatial_HAC)


```


### Format Conley SE, and save coefficients and SE

```{r}

SE<-return_list 
SE_df<-sapply(SE, function(x) diag(sqrt(abs(x)))) %>% round(3) %>% #Added abs, does not change values, just keeps headers
  data.frame() %>% 
  tibble::rownames_to_column() %>% 
  rename(Variable=rowname)

final_conley_df<-conley_coef %>% 
  dplyr::left_join(conley_cse, by="Variable") %>% 
  dplyr::left_join(SE_df, by="Variable") %>% 
  mutate(Variable=c("Percent Cropland", "Natural-Crop Edge Density", "Average Crop Area", "Proportion Large Farms",
                             "Proportion soybeans and small grains", "Proportion corn", "Proportion fruit and vegetables",
                             "Landscape Diversity", "Cropland Diversity"))
final_conley_df

#Save as csv
write_csv(final_conley_df, "Data/Visualize/conley/final_conley_df.csv")

```


## Robustness Check: <1% Cropland
Remove counties with <1% of cropland (NLCD) and run best model, reporting in supplementary section on how many observations it removes; create map showing which counties are removed

### Create and explore the <1% dataset

```{r}

load("Data/DataProcessing/df/fulldata.rda")

data_pcrop_less1perc<-fulldata %>% 
  select(FIPS, Year, ASDCode, ERSCode,
         insect_planted, pland_crops, natural_crops_ed, mna_crops, largefarm_planted,
         soysmallgrain_planted, corn_planted, fruitveg_planted,
         msidi, SDI) %>% 
    filter(!Year==2002)%>% #Only 3 years of data
  filter(pland_crops>=1) %>% 
  na.omit() %>% #6590 observations 
  mutate_at(scale, .vars=vars(-FIPS, -Year, -ERSCode, -ASDCode, -insect_planted)) %>%  #Scale by subtracting column mean and dividing by column SD
    rename(Insecticide=insect_planted,
         PercentCrop=pland_crops,
         NaturalCropEdge=natural_crops_ed,
         MeanCropArea=mna_crops,
         LargeFarms=largefarm_planted,
         SoyGrains=soysmallgrain_planted,
         Corn=corn_planted,
         FruitVeg=fruitveg_planted,
         LandDiversity=msidi,
         CropDiversity=SDI)
#Original data_natural had 8939 observations, and data_pcrop_less1perc has 6590 observations

#Dataset to compare it to is data_natural
load("Data/Analysis/models/df/data_natural.Rda")
obsdiff<-nrow(data_natural)-nrow(data_pcrop_less1perc) #2349
obspcdiff<-obsdiff/nrow(data_natural)*100 #~26% of observations lost
uniqFIPS<-length(unique(data_natural$FIPS))-length(unique(data_pcrop_less1perc$FIPS))#798

#Math to compare the datasets-figure out which FIPS different and which years
natural_subset<-data_natural %>% select(FIPS, Year) %>% mutate(Data="natural")
pcrop_subset<-data_pcrop_less1perc %>% select(FIPS, Year)%>% mutate(Data="pcrop")

merge_subset<-full_join(natural_subset, pcrop_subset, by = c("FIPS", "Year"))
rem_fips <- merge_subset[is.na(merge_subset$Data.y),] %>% #2349 rows-combo of 
  select(FIPS, Year)
uniqfips<-unique(rem_fips$FIPS)
uniqfips_num<-length(uniqfips)#838 counties
year_counts<-table(rem_fips$Year)#800 counts 2007, 776 counts 2012, 772 countes 2017

#Dataframe to combine
pcrop_df<-merge_subset %>% 
  mutate(Pcrop=ifelse(Data.y=="pcrop", 0, 1))#1 given to low crop, aka FIPS removed
pcrop_df$Pcrop[is.na(pcrop_df$Pcrop)]<- 1
pcrop_df<-pcrop_df %>% select(FIPS, Pcrop)

#Count how many times FIPS removed (how many times FIPS has a 0)
final_pcrop_df<-unique(transform(pcrop_df, Pcrop=ave(pcrop_df$Pcrop, pcrop_df$FIPS, FUN=sum)))

#Plot missing FIPS (aka FIPS with low cropland)
counties<-read_sf(dsn = "C:/Users/shemc/Documents/UCSB/NLCD/Data/TIGER2018_Counties", layer = "tl_2018_us_county") %>%  
  dplyr::mutate(FIPS=paste0(STATEFP,COUNTYFP))
counties<-st_transform(counties, "+proj=aea +lat_1=29.5 +lat_2=45.5 +lat_0=23 +lon_0=-96 +x_0=0 +y_0=0 +ellps=WGS84
                     +towgs84=0,0,0,-0,-0,-0,0 +units=m +no_defs ") #Project counties to nlcd projection
contig48_counties<-subset(counties,counties$STATEFP!="02"& counties$STATEFP!="15"&
                            counties$STATEFP!="60"&counties$STATEFP!="66"&
                            counties$STATEFP!="69"&counties$STATEFP!="72"&
                            counties$STATEFP!="74"&counties$STATEFP!="78") %>% 
  select(FIPS, geometry) %>% 
  mutate(FIPS=as.numeric(FIPS))

#Join counties data with uniqfips
pcrop_sf<-contig48_counties %>% 
  full_join(final_pcrop_df, by="FIPS") %>% 
  mutate(Pcrop=as.integer(Pcrop))


#Map by how many times FIPS removed for <1% Cropland
  tm_count<-tm_shape(pcrop_sf)+tm_fill("Pcrop", title="Numbers of years \n county is <1% cropland ",
                             breaks=c(0,1,2,3,4),
                             labels=c("0", "1", "2", "3"),
                             textNA = "No Data", colorNA = "gray80")+
    tm_borders(col = "gray40", lwd = 1)
  tmap_save(tm = tm_count, filename = "Data/Visualize/robustness/pcrop_less1pc/counties_lessthan1percentcrop_NLCD.png", dpi = 300)

```

### Run final model on <1% cropland dataset and produce stargazer table of results with cluster robust SE

```{r}

#6590 observations
lm_pcrop_less1pc<-lm(Insecticide~PercentCrop+NaturalCropEdge+MeanCropArea+LargeFarms+
                  SoyGrains+Corn+FruitVeg+LandDiversity+CropDiversity+
                  factor(Year)+factor(ASDCode), data=data_pcrop_less1perc)
df_coef_pcropless1pc<-lm_pcrop_less1pc %>% 
  clubSandwich::coef_test(vcov = "CR2", cluster = data_pcrop_less1perc$ASDCode, test = "Satterthwaite")

stargazer::stargazer(lm_pcrop_less1pc, type="text", omit=c("ASDCode","Year"), out="Data/Visualize/robustness/pcrop_less1pc/pcrop_less1pc_stargazer.txt",
                               covariate.labels=c("Percent Cropland", "Natural-Crop Edge Density", 
                                                  "Average Crop Area", "Proportion Large Farms",
                             "Proportion soybeans and small grains", "Proportion corn", "Proportion fruit and vegetables",
                             "Landscape Diversity", "Cropland Diversity"),
                     omit.stat=c("LL","ser","f"),
                     se = list(df_coef_pcropless1pc[,2]),p=list(df_coef_pcropless1pc[,5]))

```


### Quick check to <1% cropland based on harv_crop from CoA, but run regression based on NLCD

```{r}

load("Data/DataProcessing/df/fulldata.rda")

data_coa_cropless1pc<-fulldata %>% 
  select(FIPS, Year, ASDCode, ERSCode, harv_county,
         insect_planted, pland_crops, natural_crops_ed, mna_crops, largefarm_planted,
         soysmallgrain_planted, corn_planted, fruitveg_planted,
         msidi, SDI) %>% 
    filter(!Year==2002)%>% #Only 3 years of data
  filter(harv_county>=0.01) %>% 
  na.omit() %>% #8319 observations 
  mutate_at(scale, .vars=vars(-FIPS, -Year, -ERSCode, -ASDCode, -insect_planted)) %>%  #Scale by subtracting column mean and dividing by column SD
    rename(Insecticide=insect_planted,
         PercentCrop=pland_crops,
         NaturalCropEdge=natural_crops_ed,
         MeanCropArea=mna_crops,
         LargeFarms=largefarm_planted,
         SoyGrains=soysmallgrain_planted,
         Corn=corn_planted,
         FruitVeg=fruitveg_planted,
         LandDiversity=msidi,
         CropDiversity=SDI)

#8319 observations
lm_coa_cropless1pc<-lm(Insecticide~PercentCrop+NaturalCropEdge+MeanCropArea+LargeFarms+
                  SoyGrains+Corn+FruitVeg+LandDiversity+CropDiversity+
                  factor(Year)+factor(ASDCode), data=data_coa_cropless1pc)
df_coef_coa_cropless1pc<-lm_coa_cropless1pc %>% 
  clubSandwich::coef_test(vcov = "CR2", cluster = data_coa_cropless1pc$ASDCode, test = "Satterthwaite")

stargazer::stargazer(lm_coa_cropless1pc, type="text", omit=c("ASDCode","Year"), out="Data/Visualize/robustness/pcrop_less1pc/coa_cropless1pc_stargazer.txt",
                               covariate.labels=c("Percent Cropland", "Natural-Crop Edge Density", 
                                                  "Average Crop Area", "Proportion Large Farms",
                             "Proportion soybeans and small grains", "Proportion corn", "Proportion fruit and vegetables",
                             "Landscape Diversity", "Cropland Diversity"),
                     omit.stat=c("LL","ser","f"),
                     se = list(df_coef_coa_cropless1pc[,2]),p=list(df_coef_coa_cropless1pc[,5]))

```

Removing by NLCD has bigger shift in estimates than removing by CoA which has almost no shift. Probably because by CoA has very similar number of observations as best model. However, both models are "improved", as they have R2 values of ~0.74, about 0.04 higher than best model (natural model).

## Robustness Check: Percent Crop (NLCD) vs Harvested Crop (CoA)
Replaced percent crop (NLCD) with harvested crop per county (CoA) and re-run best model to identify if results change

```{r}

load("Data/DataProcessing/df/fulldata.rda")

data_harvcrop<-fulldata %>% 
  select(FIPS, Year, ASDCode, ERSCode, harv_county,
         insect_planted, pland_crops, natural_crops_ed, mna_crops, largefarm_planted,
         soysmallgrain_planted, corn_planted, fruitveg_planted,
         msidi, SDI) %>% 
    filter(!Year==2002)%>% #Only 3 years of data
  na.omit() %>% #8939 observations (same as data_natural)
  mutate_at(scale, .vars=vars(-FIPS, -Year, -ERSCode, -ASDCode, -insect_planted)) %>%  #Scale by subtracting column mean and dividing by column SD
    rename(Insecticide=insect_planted,
         HarvestedCropland=harv_county,
         NaturalCropEdge=natural_crops_ed,
         MeanCropArea=mna_crops,
         LargeFarms=largefarm_planted,
         SoyGrains=soysmallgrain_planted,
         Corn=corn_planted,
         FruitVeg=fruitveg_planted,
         LandDiversity=msidi,
         CropDiversity=SDI)

#8939 observations
lm_harvcrop<-lm(Insecticide~HarvestedCropland+NaturalCropEdge+MeanCropArea+LargeFarms+
                  SoyGrains+Corn+FruitVeg+LandDiversity+CropDiversity+
                  factor(Year)+factor(ASDCode), data=data_harvcrop)
df_coef_harvcrop<-lm_harvcrop %>% 
  clubSandwich::coef_test(vcov = "CR2", cluster = data_harvcrop$ASDCode, test = "Satterthwaite")

stargazer::stargazer(lm_harvcrop, type="text", omit=c("ASDCode","Year"),
                     out="Data/Visualize/robustness/harvcrop/harvcrop_stargazer.txt",
                               covariate.labels=c("Proportion Harvested Cropland", "Natural-Crop Edge Density", 
                                                  "Average Crop Area", "Proportion Large Farms",
                             "Proportion soybeans and small grains", "Proportion corn", "Proportion fruit and vegetables",
                             "Landscape Diversity", "Cropland Diversity"),
                     omit.stat=c("LL","ser","f"),
                     se = list(df_coef_harvcrop[,2]),p=list(df_coef_harvcrop[,5]))

```

Almost identical results, only the sign switched for average crop area, and a few are very slightly different.
Harv_crop and pland crops almost identical estimates.
Not investigating <1% cropland on this model, because should be very similar to effect seen when using pland_crop.


##Robusntess Check: Combine Above Models
```{r}

#Read in natural for comparison
load("Data/Analysis/models/lm_natural.Rda")
df_coef_natural<-lm_natural %>% 
  clubSandwich::coef_test(vcov = "CR2", cluster = data_natural$ASDCode, test = "Satterthwaite")

#Version of harvcrop with same percentcrop name
data_harvcrop_comb<-fulldata %>% 
  select(FIPS, Year, ASDCode, ERSCode, harv_county,
         insect_planted, pland_crops, natural_crops_ed, mna_crops, largefarm_planted,
         soysmallgrain_planted, corn_planted, fruitveg_planted,
         msidi, SDI) %>% 
    filter(!Year==2002)%>% #Only 3 years of data
  na.omit() %>% #8939 observations (same as data_natural)
  mutate_at(scale, .vars=vars(-FIPS, -Year, -ERSCode, -ASDCode, -insect_planted)) %>%  #Scale by subtracting column mean and dividing by column SD
    rename(Insecticide=insect_planted,
         PercentCrop=harv_county,
         NaturalCropEdge=natural_crops_ed,
         MeanCropArea=mna_crops,
         LargeFarms=largefarm_planted,
         SoyGrains=soysmallgrain_planted,
         Corn=corn_planted,
         FruitVeg=fruitveg_planted,
         LandDiversity=msidi,
         CropDiversity=SDI)

#8939 observations
lm_harvcrop_comb<-lm(Insecticide~PercentCrop+NaturalCropEdge+MeanCropArea+LargeFarms+
                  SoyGrains+Corn+FruitVeg+LandDiversity+CropDiversity+
                  factor(Year)+factor(ASDCode), data=data_harvcrop_comb)
df_coef_harvcrop_comb<-lm_harvcrop_comb %>% 
  clubSandwich::coef_test(vcov = "CR2", cluster = data_harvcrop_comb$ASDCode, test = "Satterthwaite")

#Stargazer of results together
stargazer::stargazer(lm_natural, lm_pcrop_less1pc, lm_coa_cropless1pc, lm_harvcrop_comb, type="text", omit=c("ASDCode","Year"),
                     out="Data/Visualize/robustness/robustmodels_stargazer.txt",
                               covariate.labels=c("Percent Cropland", "Natural-Crop Edge Density", 
                                                  "Average Crop Area", "Proportion Large Farms",
                             "Proportion soybeans and small grains", "Proportion corn", "Proportion fruit and vegetables",
                             "Landscape Diversity", "Cropland Diversity"),
                     omit.stat=c("LL","ser","f"),
                     se = list(df_coef_natural[,2],df_coef_pcropless1pc[,2],df_coef_coa_cropless1pc[,2],df_coef_harvcrop_comb[,2]),
                     p=list(df_coef_natural[,5],df_coef_pcropless1pc[,5],df_coef_coa_cropless1pc[,5],df_coef_harvcrop_comb[,5]))


```



## Robustness Check: Fixed Effects County vs ASD
Run best model with fixed effects on county instead of ASD for supplementary figure, including table of xtsum output showing ASD better than county level in terms of remaining variation

```{r}

#Use data_natural, only changing the lm model
load("Data/Analysis/models/df/data_natural.Rda")

#8939 observations
lm_FIPS<-lm(Insecticide~PercentCrop+NaturalCropEdge+MeanCropArea+LargeFarms+
                  SoyGrains+Corn+FruitVeg+LandDiversity+CropDiversity+
                  factor(Year)+factor(FIPS), data=data_natural)
#Saved to put on R server online

#Cluster around ASDCode because FIPS too many, won't work-ran on R server so faster
# df_coef_FIPS<-lm_FIPS%>%
#   clubSandwich::coef_test(vcov = "CR2", cluster = data_natural$ASDCode, test = "Satterthwaite")
load("Data/Visualize/robustness/FIPS/df_coef_FIPS.Rda")



stargazer::stargazer(lm_FIPS, type="text", omit=c("FIPS","Year"),
                     out="Data/Visualize/robustness/FIPS/FIPS_stargazer.txt",
                               covariate.labels=c("Percent Cropland", "Natural-Crop Edge Density", 
                                                  "Average Crop Area", "Proportion Large Farms",
                             "Proportion soybeans and small grains", "Proportion corn", "Proportion fruit and vegetables",
                             "Landscape Diversity", "Cropland Diversity"),
                     omit.stat=c("LL","ser","f"),
                     se = list(df_coef_FIPS[,2]),p=list(df_coef_FIPS[,5]))


```

Another reason to justify moving from FIPS to ASDCode is the processing speed. For clustering, clustering around 303 ASD vs 3031 FIPS (for data_natural dataset). Faster processing, less memory storage.

## CoA only cross-sectional models
Retrive CoA data back to 1987 and create boxplots and run cross-sectional models on CoA data (large farm, crop covariates, harvested crop) from 1987-2017

WAIT UNTIL CAN ACCESS 1987 AND 1992 COA DATA
Currently setting it up with 1997-2017 data

```{r}

load("Data/DataProcessing/df/fulldata.rda")

data_coa<-fulldata %>% 
  select(FIPS, Year, ASDCode, ERSCode,
         insect_planted, harv_county, largefarm_planted,
         soysmallgrain_planted, corn_planted, fruitveg_planted) %>% 
  na.omit() %>% #14938 observations
  mutate_at(scale, .vars=vars(-FIPS, -Year, -ERSCode, -ASDCode, -insect_planted)) %>%  #Scale by subtracting column mean and dividing by column SD
    rename(Insecticide=insect_planted,
         HarvestedCrop=harv_county,
         LargeFarms=largefarm_planted,
         SoyGrains=soysmallgrain_planted,
         Corn=corn_planted,
         FruitVeg=fruitveg_planted)

lm_coa<-lm(Insecticide~HarvestedCrop+LargeFarms+SoyGrains+Corn+FruitVeg+factor(Year)+factor(ASDCode), data=data_coa)
df_coef_coa<-lm_coa%>% clubSandwich::coef_test(vcov = "CR2", cluster = data_coa$ASDCode, test = "Satterthwaite")

stargazer::stargazer(lm_coa, type="text", omit=c("ASDCode","Year"),
                     out="Data/Visualize/coa/coa_stargazer.txt",
                               covariate.labels=c("Harvested Cropland", "Proportion Large Farms",
                             "Proportion soybeans and small grains", "Proportion corn", "Proportion fruit and vegetables"),
                     omit.stat=c("LL","ser","f"),
                     se = list(df_coef_coa[,2]),p=list(df_coef_coa[,5]))


#By year, with spatial fixed effects
data_coa_1997<-data_coa %>% filter(Year==1997)
data_coa_2002<-data_coa %>% filter(Year==2002)
data_coa_2007<-data_coa %>% filter(Year==2007)
data_coa_2012<-data_coa %>% filter(Year==2012)
data_coa_2017<-data_coa %>% filter(Year==2017)


#Models by year
lm_coa_1997<-lm(Insecticide~HarvestedCrop+LargeFarms+SoyGrains+Corn+FruitVeg+factor(ASDCode), data=data_coa_1997)
lm_coa_2002<-lm(Insecticide~HarvestedCrop+LargeFarms+SoyGrains+Corn+FruitVeg+factor(ASDCode), data=data_coa_2002)
lm_coa_2007<-lm(Insecticide~HarvestedCrop+LargeFarms+SoyGrains+Corn+FruitVeg+factor(ASDCode), data=data_coa_2007)
lm_coa_2012<-lm(Insecticide~HarvestedCrop+LargeFarms+SoyGrains+Corn+FruitVeg+factor(ASDCode), data=data_coa_2012)
lm_coa_2017<-lm(Insecticide~HarvestedCrop+LargeFarms+SoyGrains+Corn+FruitVeg+factor(ASDCode), data=data_coa_2017)

#CRSE by year
df_coef_coa_1997<-lm_coa_1997%>% clubSandwich::coef_test(vcov = "CR2", cluster = data_coa_1997$ASDCode, test = "Satterthwaite")
df_coef_coa_2002<-lm_coa_2002%>% clubSandwich::coef_test(vcov = "CR2", cluster = data_coa_2002$ASDCode, test = "Satterthwaite")
df_coef_coa_2007<-lm_coa_2007%>% clubSandwich::coef_test(vcov = "CR2", cluster = data_coa_2007$ASDCode, test = "Satterthwaite")
df_coef_coa_2012<-lm_coa_2012%>% clubSandwich::coef_test(vcov = "CR2", cluster = data_coa_2012$ASDCode, test = "Satterthwaite")
df_coef_coa_2017<-lm_coa_2017%>% clubSandwich::coef_test(vcov = "CR2", cluster = data_coa_2017$ASDCode, test = "Satterthwaite")

#Stargazer table of results
stargazer::stargazer(lm_coa_1997, lm_coa_2002, lm_coa_2007, lm_coa_2012, lm_coa_2017,
                     type="text", omit=c("ASDCode","Year"),
                     out="Data/Visualize/coa/coa_year_stargazer.txt",
                     covariate.labels=c("Harvested Cropland", "Proportion Large Farms",
                             "Proportion soybeans and small grains", "Proportion corn", "Proportion fruit and vegetables"),
                     omit.stat=c("LL","ser","f"),
                     se = list(df_coef_coa_1997[,2],df_coef_coa_2002[,2],df_coef_coa_2007[,2],df_coef_coa_2012[,2],df_coef_coa_2017[,2]),
                     p=list(df_coef_coa_1997[,5],df_coef_coa_2002[,5],df_coef_coa_2007[,5],df_coef_coa_2012[,5],df_coef_coa_2017[,5]),
                     column.labels=c("1997", "2002", "2007", "2012", "2017"), model.numbers=FALSE)

```

 
## Create Model Versions with Only Percent Cropland and Percent Cropland & Cropland Diversity

```{r}

#Based off natural dataset so easier to compare results
data_pcrop<-fulldata %>% 
  select(FIPS, Year, ASDCode, ERSCode,
         insect_planted, pland_crops, natural_crops_ed, mna_crops, largefarm_planted,
         soysmallgrain_planted, corn_planted, fruitveg_planted,
         msidi, SDI) %>% 
    filter(!Year==2002)%>% #Only 3 years of data
  na.omit() %>% #8939 observations (match crops_3yrs and diversity)
  select(FIPS, Year, ASDCode, ERSCode,insect_planted, pland_crops) %>% 
  mutate_at(scale, .vars=vars(-FIPS, -Year, -ERSCode, -ASDCode, -insect_planted)) %>%  #Scale by subtracting column mean and dividing by column SD
    rename(Insecticide=insect_planted,
         PercentCrop=pland_crops)

lm_pcrop<-lm(Insecticide~PercentCrop+factor(Year)+factor(ASDCode), data=data_pcrop)
df_coef_pcrop<-lm_pcrop%>% clubSandwich::coef_test(vcov = "CR2", cluster = data_pcrop$ASDCode, test = "Satterthwaite")
stargazer::stargazer(lm_pcrop, type="text", omit=c("ASDCode","Year"),
                     out="Data/Visualize/simple/pcrop_stargazer.txt",
                               covariate.labels=c("Percent Cropland"),
                     omit.stat=c("LL","ser","f"),se = list(df_coef_pcrop[,2]),p=list(df_coef_pcrop[,5]))
#not as good of a model, R2 only .6 compared to ~.7 or higher in other final models



#Based off natural dataset so easier to compare results
data_pcrop_cdl<-fulldata %>% 
  select(FIPS, Year, ASDCode, ERSCode,
         insect_planted, pland_crops, natural_crops_ed, mna_crops, largefarm_planted,
         soysmallgrain_planted, corn_planted, fruitveg_planted,
         msidi, SDI) %>% 
    filter(!Year==2002)%>% #Only 3 years of data
  na.omit() %>% #8939 observations (match crops_3yrs and diversity)
  select(FIPS, Year, ASDCode, ERSCode,insect_planted, pland_crops, SDI) %>% 
  mutate_at(scale, .vars=vars(-FIPS, -Year, -ERSCode, -ASDCode, -insect_planted)) %>%  #Scale by subtracting column mean and dividing by column SD
    rename(Insecticide=insect_planted,
         PercentCrop=pland_crops,
         CropDiversity=SDI)

lm_pcrop_cdl<-lm(Insecticide~PercentCrop+CropDiversity+factor(Year)+factor(ASDCode), data=data_pcrop_cdl)
df_coef_pcrop_cdl<-lm_pcrop_cdl%>% clubSandwich::coef_test(vcov = "CR2", cluster = data_pcrop_cdl$ASDCode, test = "Satterthwaite")
stargazer::stargazer(lm_pcrop_cdl, type="text", omit=c("ASDCode","Year"),
                     out="Data/Visualize/simple/pcrop_cdl_stargazer.txt",
                               covariate.labels=c("Percent Cropland", "Cropland Diversity"),
                     omit.stat=c("LL","ser","f"),se = list(df_coef_pcrop_cdl[,2]),p=list(df_coef_pcrop_cdl[,5]))
#not as good of a model, R2 only .6 compared to ~.7 or higher in other final models; better than just cropland but not as good

```

