---
title: "Visualize"
author: "Sofie McComb"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This R Markdown will be used to visualize the data and results developed from the Analysis.Rmd.

### Load Packages

```{r packages, message=F, warning=F}

#Load the needed packages (install first if necessary)
library(ggplot2) #data visualization
library(ggpubr)#To arrange ggplots on a page
library(stringr)#String detection
library(tidyverse) #Datatable manipulation (all functions)
library(dotwhisker) #relabel predictors
library(stargazer) #Create stargazer tables

#Set options
  options(scipen=999) #no scientific notation (all)

```

### Load Data

```{r load data, message=F, warning=F}

#Load fulldata
load("Data/DataProcessing/df/fulldata.rda")

#Coef results
basemodels_df_coef<-readr::read_csv("Data/Analysis/df/basemodels_df_coef.csv")
df_coef_diversity<-readr::read_csv("Data/Analysis/df/df_coef_diversity.csv")
edgemodels_df_coef<-readr::read_csv("Data/Analysis/df/edgemodels_df_coef.csv")
df_coef_regional<-readr::read_csv("Data/Analysis/df/df_coef_regional.csv")

```

##Boxplots of variables

### Boxplots of time trends of covariates

Creating boxplots showing the values for each of the variables being considered in any of the regression models, across the years being considered. Using the fulldata datasets (loaded in the variable_time_boxplots.R script sourced below).


```{r var boxplots, message=F, warning=F}

#Source R script to create boxplot visualizations
source("R/Visualize/variable_time_boxplots.R")

#Create boxplots for variables of interest (NA values will be removed)
insect_plot<-var_boxplot(variable=fulldata$insect_planted, yaxis="Prop. Cropland w/ Insecticides")
plandcrops_plot<-var_boxplot(variable=fulldata$pland_crops, yaxis="Prop. of Cty in Cropland")
edgecrops_plot<-var_boxplot(variable=fulldata$ed_crops, yaxis="Crop Edge Density (m/ha)")
mnacrops_plot<-var_boxplot(variable=fulldata$mna_crops, yaxis="Avg. Acreage of Crop Patches (ha)")
largefarm_plot<-var_boxplot(variable=fulldata$largefarm_planted, yaxis="Prop. of Cropland with Lg. Farms")
soygrain_plot<-var_boxplot(variable=fulldata$soysmallgrain_planted, yaxis="Prop. Soybeans & Sm. Grains")
corn_plot<-var_boxplot(variable=fulldata$corn_planted, yaxis="Prop. Corn")
fruitveg_plot<-var_boxplot(variable=fulldata$fruitveg_planted, yaxis="Prop. Fruit & Veg.")
msidi_plot<-var_boxplot(variable=fulldata$msidi, yaxis="Landscape Diversity")
SDI_plot<-var_boxplot(variable=fulldata$SDI, yaxis="Crop Diversity")
ncedge_plot<-var_boxplot(variable=fulldata$natural_crops_ed, yaxis="Natural to Crop Land Edges")
fcedge_plot<-var_boxplot(variable=fulldata$forest_crops_ed , yaxis="Forest to Crop Land Edges")
sgcedge_plot<-var_boxplot(variable=fulldata$shrubgrass_crops_ed , yaxis="Shrubland and Grassland to Crop Land Edges")

#Save insecticides plot
ggexport(insect_plot, filename = "Data/Visualize/boxplots/insecticides_timetrends_boxplots.png")

#Arrange boxplots on one page
allvarplots<-ggarrange(plandcrops_plot,edgecrops_plot,
              mnacrops_plot, largefarm_plot, 
              soygrain_plot, corn_plot, fruitveg_plot,
              msidi_plot,SDI_plot, 
             ncedge_plot, fcedge_plot, sgcedge_plot,
          labels = c("A", "B", "C", "D", "E", "F", "G", "H", "I", "J", "K"),
          ncol = 4, nrow = 3)

#Save the combined variable boxplots page
ggexport(allvarplots, filename = "Data/Visualize/boxplots/allvariables_timetrends_boxplots.png",
          width = 1800, height = 1500)

```


### Boxplots of spatial trends of covariates

Creating boxplots showing the values for each of the variables being considered in any of the regression models, across the ERS being considered. Using the fulldata datasets (loaded in the variable_spatial_boxplots.R script sourced below).


```{r var boxplots spatial, message=F, warning=F}

#Source R script to create boxplot visualizations
#Load fulldata to pull from
load("Data/DataProcessing/df/fulldata.rda")
fulldata_nona<-fulldata %>% 
  drop_na(ERSCode)

source("R/Visualize/variable_spatial_boxplots.R")

#Create boxplots for variables of interest (NA values will be removed)
insect_plot<-var_boxplot(variable=fulldata_nona$insect_planted, yaxis="Prop. Cropland w/ Insecticides")
plandcrops_plot<-var_boxplot(variable=fulldata_nona$pland_crops, yaxis="Prop. of Cty in Cropland")
edgecrops_plot<-var_boxplot(variable=fulldata_nona$ed_crops, yaxis="Crop Edge Density (m/ha)")
mnacrops_plot<-var_boxplot(variable=fulldata_nona$mna_crops, yaxis="Avg. Acreage of Crop Patches (ha)")
largefarm_plot<-var_boxplot(variable=fulldata_nona$largefarm_planted, yaxis="Prop. of Cropland with Lg. Farms")
soygrain_plot<-var_boxplot(variable=fulldata_nona$soysmallgrain_planted, yaxis="Prop. Soybeans & Sm. Grains")
corn_plot<-var_boxplot(variable=fulldata_nona$corn_planted, yaxis="Prop. Corn")
fruitveg_plot<-var_boxplot(variable=fulldata_nona$fruitveg_planted, yaxis="Prop. Fruit & Veg.")
msidi_plot<-var_boxplot(variable=fulldata_nona$msidi, yaxis="Landscape Diversity")
SDI_plot<-var_boxplot(variable=fulldata_nona$SDI, yaxis="Crop Diversity")
ncedge_plot<-var_boxplot(variable=fulldata_nona$natural_crops_ed, yaxis="Natural to Crop Land Edges")
fcedge_plot<-var_boxplot(variable=fulldata_nona$forest_crops_ed , yaxis="Forest to Crop Land Edges")
sgcedge_plot<-var_boxplot(variable=fulldata_nona$shrubgrass_crops_ed , yaxis="Shrubland and Grassland to Crop Land Edges")

#Save insecticides plot
ggexport(insect_plot, filename = "Data/Visualize/boxplots/insecticides_spatialtrends_boxplots.png")

#Arrange boxplots on one page
allvarplots<-ggarrange(plandcrops_plot,edgecrops_plot,
              mnacrops_plot, largefarm_plot, 
              soygrain_plot, corn_plot, fruitveg_plot,
              msidi_plot,SDI_plot, 
             ncedge_plot, fcedge_plot, sgcedge_plot,
          labels = c("A", "B", "C", "D", "E", "F", "G", "H", "I", "J", "K"),
          ncol = 4, nrow = 3)

#Save the combined variable boxplots page
ggexport(allvarplots, filename = "Data/Visualize/boxplots/allvariables_spatialtrends_boxplots.png",
          width = 1800, height = 1500)

```


## Errorbar charts for different analyses

### Landscape composition and configuration

```{r}

#Plot basemodels on x and coefficient for each model with SD facet by term
#Relabel predictors
basemodels_plot_df <- basemodels_df_coef %>%
  relabel_predictors(c(PercentCrop = "Percent Cropland",
                       CropEdge= "Crop Edge Density",
                       MeanCropArea = "Avg. Crop Area",
                       LargeFarms = " Proportion Large Farm",
                       SoyGrains= "Proportion Soy & Grains",
                       Corn= "Proportion Corn",
                       FruitVeg= "Proportion Fruit & Veg"))

basemodels_compare<-ggplot2::ggplot(basemodels_plot_df, aes(x = model, color=model)) +
  geom_errorbar(aes(ymax = estimate + std.error, ymin = estimate - std.error),
                position = "dodge", width=0.5, size=1)+
  geom_point(aes(y=estimate), size=3)+
   geom_hline(yintercept = 0, colour = "grey60", linetype = 2) +
  theme_bw() + ylab("Coefficient Estimate")+ labs(color="Model")+xlab("")+
  facet_wrap(~term)+
  theme(text = element_text(size = 18),
            axis.text.x=element_blank(),
            axis.title = element_text(size=22),
          strip.text.x = element_text(size = 20),
            legend.title=element_text(size=22),
          legend.text=element_text(size=20))+
  scale_colour_manual(values=c("#007ed8", "#8bb860","#cb8f00","#b40000"),labels = c("With Crops, 3yrs data", "With Crops, 4yrs data", "Without Crops, 3yrs data", "Without Crops, 4yrs data"))

ggexport(basemodels_compare, filename = "Data/Visualize/boxwhisker/basemodels_compare.png",
             width = 1500, height = 1200)


```


### Diversity

```{r}

#Plot diversity on x and coefficient on y with SD facet by term
#Relabel predictors
diversity_plot_df <- df_coef_diversity %>%
  relabel_predictors(c(PercentCrop = "Percent Cropland",
                       CropEdge= "Crop Edge Density",
                       MeanCropArea = "Avg. Crop Area",
                       LargeFarms = " Proportion Large Farm",
                       SoyGrains= "Proportion Soy & Grains",
                       Corn= "Proportion Corn",
                       FruitVeg= "Proportion Fruit & Veg",
                       LandDiversity= "Landscape Diversity",
                       CropDiversity="Cropland Diversity"))

diversity_compare<-ggplot2::ggplot(diversity_plot_df, aes(y=fct_rev(as_factor(term)))) +
  geom_errorbarh(aes(xmax = estimate + std.error, xmin = estimate - std.error),
                height=0.3, size=1, colour="royalblue")+
  geom_point(aes(x=estimate), size=2, colour="royalblue")+
  geom_vline(xintercept = 0, colour = "grey60", linetype = 2) +
  theme_bw() + ylab("")+xlab("Coefficient Estimate")+
  theme(text = element_text(size = 20))

  ggexport(diversity_compare, filename = "Data/Visualize/boxwhisker/diversity_compare.png",
           width = 900, height = 800)

```


### Edge Interactions

```{r}

#Plot edgemodels on x and coefficient for each model with SD facet by term
#Relabel predictors
edgemodels_plot_df <- edgemodels_df_coef %>%
  relabel_predictors(c(PercentCrop = "Percent Cropland",
                       MeanCropArea = "Avg. Crop Area",
                       LargeFarms = "Proportion Large Farm",
                       SoyGrains= "Proportion Soy & Grains",
                       Corn= "Proportion Corn",
                       FruitVeg= "Proportion Fruit & Veg",
                       LandDiversity= "Landscape Diversity",
                       CropDiversity="Cropland Diversity",
                       NaturalCropEdge= "Natural-Crop Edge Density",
                       ForestCropEdge= "Forest-Crop Edge Density",
                       ShrubgrassCropEdge= "Shrubgrass-Crop Edge Density")) %>% 
  mutate(modelorder=as.factor(ifelse(model=="natural", 1, ifelse(model=="forest", 2, ifelse(model=="shrubgrass", 3, 0))))) %>% 
  arrange(modelorder) %>% 
  mutate(term=as.factor(term))
         
  edgemodels_plot_df$term<-factor(edgemodels_plot_df$term,
                                  levels=c("Percent Cropland","Avg. Crop Area", "Proportion Large Farm",
                           "Proportion Soy & Grains","Proportion Corn","Proportion Fruit & Veg",
                           "Landscape Diversity","Cropland Diversity","Natural-Crop Edge Density",
                           "Forest-Crop Edge Density","Shrubgrass-Crop Edge Density"))


edgemodels_compare<-ggplot2::ggplot(edgemodels_plot_df, aes(x = modelorder, color=modelorder)) +
  geom_errorbar(aes(ymax = estimate + std.error, ymin = estimate - std.error),
                position = "dodge", width=0.5, size=1)+
   geom_point(aes(y=estimate), size=3)+
   geom_hline(yintercept = 0, colour = "grey60", linetype = 2) +
  theme_bw() + ylab("Coefficient Estimate")+ labs(color="Model")+xlab("")+
  facet_wrap(~term)+
  theme(text = element_text(size = 18),
            axis.text.x=element_blank(),
            axis.title = element_text(size=22),
          strip.text.x = element_text(size = 20),
            legend.title=element_text(size=22),
          legend.text=element_text(size=20))+
  scale_colour_manual(values=c("#007ed8","#8bb860", "#0d98ba"),labels = c("Natural", "Forest", "Shrub & Grass"))

 ggexport(edgemodels_compare, filename = "Data/Visualize/boxwhisker/edgemodels_compare.png",
             width = 1500, height = 1200)
 
 ####################
 #Version add edge_crop in
 alledgemodels_plot_df <- rbind(df_coef_diversity, edgemodels_df_coef) %>%
  relabel_predictors(c(PercentCrop = "Percent Cropland",
                       CropEdge= "Crop Edge Density",
                       MeanCropArea = "Avg. Crop Area",
                       LargeFarms = " Proportion Large Farm",
                       SoyGrains= "Proportion Soy & Grains",
                       Corn= "Proportion Corn",
                       FruitVeg= "Proportion Fruit & Veg",
                       LandDiversity= "Landscape Diversity",
                       CropDiversity="Cropland Diversity",
                       NaturalCropEdge= "Natural-Crop Edge Density",
                       ForestCropEdge= "Forest-Crop Edge Density",
                       ShrubgrassCropEdge= "Shrubgrass-Crop Edge Density")) %>% 
     mutate(modelorder=as.factor(ifelse(model=="diversity", 1, 
                                        ifelse(model=="natural", 2, 
                                               ifelse(model=="forest", 3,
                                                      ifelse(model=="shrubgrass", 4, 0)))))) %>% 
   arrange(modelorder) %>% 
   mutate(term=as.factor(term))
         
  # alledgemodels_plot_df$term<-factor(alledgemodels_plot_df$term,
  #                                 levels=c("Percent Cropland","Avg. Crop Area", "Proportion Large Farm",
  #                          "Proportion Soy & Grains","Proportion Corn","Proportion Fruit & Veg",
  #                          "Landscape Diversity","Cropland Diversity","Crop Edge Density", "Natural-Crop Edge Density",
  #                          "Forest-Crop Edge Density","Shrubgrass-Crop Edge Density"))
 
 #Struggling to relevel the facet wrap-creating NAs

 alledgemodels_compare<-ggplot2::ggplot(alledgemodels_plot_df, aes(x = modelorder, color=modelorder)) +
  geom_errorbar(aes(ymax = estimate + std.error, ymin = estimate - std.error),
                position = "dodge", width=0.5, size=1)+
   geom_point(aes(y=estimate), size=3)+
   geom_hline(yintercept = 0, colour = "grey60", linetype = 2) +
  theme_bw() + ylab("Coefficient Estimate")+ labs(color="Model")+xlab("")+
  facet_wrap(~term)+
  theme(text = element_text(size = 18),
            axis.text.x=element_blank(),
            axis.title = element_text(size=22),
          strip.text.x = element_text(size = 20),
            legend.title=element_text(size=22),
          legend.text=element_text(size=20))+
  scale_colour_manual(values=c("#cb8f00","#007ed8","#8bb860", "#0d98ba"),labels = c("Crop", "Natural", "Forest", "Shrub & Grass"))

 ggexport(alledgemodels_compare, filename = "Data/Visualize/boxwhisker/alledgemodels_compare.png",
             width = 1500, height = 1200)
 

```



### Regional Effects

```{r}

#Plot ERS on x and coefficient for each model with SD facet by term
regionalmodels_plot_df <- df_coef_regional%>%
  relabel_predictors(c(PercentCrop = "Percent Cropland",
                       NaturalCropEdge= "Natural-Crop Edge Density",
                       MeanCropArea = "Avg. Crop Area",
                       LargeFarms = "Proportion Large Farm",
                       SoyGrains= "Proportion Soy & Grains",
                       Corn= "Proportion Corn",
                       FruitVeg= "Proportion Fruit & Veg",
                       LandDiversity= "Landscape Diversity",
                       CropDiversity="Cropland Diversity"))

#Plot ERS on x and coefficient for each model with SD facet by term
cbPalette <- c("#ffd447", "#ff8787", "#cdc89e", "#eeaa55", "#a5a5a5", "#a6d1ef", "#72c377", "#c3aa1b", "#ac842b")
#The colors of the ERS map created by the USDA

regionalmodels_compare<-ggplot2::ggplot(regionalmodels_plot_df, aes(x = factor(ERS), color = factor(ERS))) +
  geom_errorbar(aes(ymax = estimate + std.error, ymin = estimate - std.error),
                position = "dodge",width=0.5, size=1)+
  geom_point(aes(y=estimate), size=3)+
  facet_wrap(~term)+
   geom_hline(yintercept = 0, colour = "grey60", linetype = 2) +
  theme_bw() + ylab("Coefficient Estimate") + xlab("ERS")+ 
  # labs(color="Model")+
  theme(text = element_text(size = 20),
            # axis.text.x=element_blank(),
            axis.title = element_text(size=22),
          strip.text.x = element_text(size = 20),
          #   legend.title=element_text(size=22),
          # legend.text=element_text(size=20),
        legend.position = "none")+
  scale_color_manual(values=cbPalette)


ggexport(regionalmodels_compare, filename = "Data/Visualize/boxwhisker/regionalmodels_compare.png",
             width = 1500, height = 1200)



```




## Create Stargazer Tables for Different Analyses

Re-run some of the lm and clubsandwich results in order to create into tables

### Load models and re-run shortened coef_test

```{r}

#Load all models from models folder
load("Data/Analysis/models/lm_nocrops_4yrs.Rda")
load("Data/Analysis/models/lm_nocrops_3yrs.Rda")
load("Data/Analysis/models/lm_crops_4yrs.Rda")
load("Data/Analysis/models/lm_crops_3yrs.Rda")
load("Data/Analysis/models/lm_diversity.Rda")
load("Data/Analysis/models/lm_natural.Rda")
load("Data/Analysis/models/lm_forest.Rda")
load("Data/Analysis/models/lm_shrubgrass.Rda")
load("Data/Analysis/models/lm_regional.Rda")

#Load all dataframes from models/df folder
load("Data/Analysis/models/df/data_nocrops_4yrs.Rda")
load("Data/Analysis/models/df/data_nocrops_3yrs.Rda")
load("Data/Analysis/models/df/data_crops_4yrs.Rda")
load("Data/Analysis/models/df/data_crops_3yrs.Rda")
load("Data/Analysis/models/df/data_diversity.Rda")
load("Data/Analysis/models/df/data_natural.Rda")
load("Data/Analysis/models/df/data_forest.Rda")
load("Data/Analysis/models/df/data_shrubgrass.Rda")
load("Data/Analysis/models/df/data_regional.Rda")

#Shortened coef_test
df_coef_nocrops_3yrs<-lm_nocrops_3yrs %>% 
  clubSandwich::coef_test(vcov = "CR2", cluster = data_nocrops_3yrs$ASDCode, test = "Satterthwaite")
df_coef_nocrops_4yrs<-lm_nocrops_4yrs %>% 
  clubSandwich::coef_test(vcov = "CR2", cluster = data_nocrops_4yrs$ASDCode, test = "Satterthwaite")
df_coef_crops_4yrs<-lm_crops_4yrs %>% 
  clubSandwich::coef_test(vcov = "CR2", cluster = data_crops_4yrs$ASDCode, test = "Satterthwaite")
df_coef_crops_3yrs<-lm_crops_3yrs %>% 
  clubSandwich::coef_test(vcov = "CR2", cluster = data_crops_3yrs$ASDCode, test = "Satterthwaite")
df_coef_diversity<-lm_diversity %>% 
  clubSandwich::coef_test(vcov = "CR2", cluster = data_diversity$ASDCode, test = "Satterthwaite")
df_coef_natural<-lm_natural %>% 
  clubSandwich::coef_test(vcov = "CR2", cluster = data_natural$ASDCode, test = "Satterthwaite")
df_coef_forest<-lm_forest %>% 
  clubSandwich::coef_test(vcov = "CR2", cluster = data_forest$ASDCode, test = "Satterthwaite")
df_coef_shrubgrass<-lm_shrubgrass %>% 
  clubSandwich::coef_test(vcov = "CR2", cluster = data_shrubgrass$ASDCode, test = "Satterthwaite")
df_coef_regional<-lm_regional %>% 
  clubSandwich::coef_test(vcov = "CR2", cluster = data_regional$ASDCode, test = "Satterthwaite")

```



### Create Tables

```{r stargazer}

stargazer(lm_nocrops_4yrs,lm_nocrops_3yrs, lm_crops_4yrs, lm_crops_3yrs, omit=c("ASDCode","Year"), 
          type = 'text', out = 'Data/Visualize/stargazer/basemodels_table.txt',
          covariate.labels=c("Percent Cropland", "Crop Edge Density", "Average Crop Area", "Proportion Large Farms", 
                             "Proportion soybeans and small grains", "Proportion corn", "Proportion fruit and vegetables"),
          omit.stat=c("LL","ser","f"), 
          se = list(df_coef_nocrops_4yrs[,2],df_coef_nocrops_3yrs[,2],df_coef_crops_4yrs[,2],df_coef_crops_3yrs[,2]),
          p=list(df_coef_nocrops_4yrs[,5],df_coef_nocrops_3yrs[,5],df_coef_crops_4yrs[,5],df_coef_crops_3yrs[,5]))


```

